### 2020-04-09 Submission1.tex
Updated first two sections - still work in progress

\documentclass[11pt]{article}

    \usepackage[breakable]{tcolorbox}
    \usepackage{parskip} % Stop auto-indenting (to mimic markdown behaviour)

    \usepackage{iftex}
    \ifPDFTeX
    	\usepackage[T1]{fontenc}
    	\usepackage{mathpazo}
    \else
    	\usepackage{fontspec}
    \fi

    \usepackage{graphicx} %package to manage images
    \graphicspath{ {./images/} }
    \usepackage{wrapfig}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % Maintain compatibility with old templates. Remove in nbconvert 6.0
    \let\Oldincludegraphics\includegraphics
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionFormat{nocaption}{}
    \captionsetup{format=nocaption,aboveskip=0pt,belowskip=0pt}

    \usepackage[Export]{adjustbox} % Used to constrain images to a maximum size
    \adjustboxset{max size={0.9\linewidth}{0.9\paperheight}}
    \usepackage{float}
    \floatplacement{figure}{H} % forces figures to be placed at the correct location
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range
    \makeatletter % fix for grffile with XeLaTeX
    \def\Gread@@xetex#1{%
      \IfFileExists{"\Gin@base".bb}%
      {\Gread@eps{\Gin@base.bb}}%
      {\Gread@@xetex@aux#1}%
    }
    \makeatother

    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    % The default LaTeX title has an obnoxious amount of whitespace. By default,
    % titling removes some of it. It also provides customization options.
    \usepackage{titling}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines
    \usepackage{mathrsfs}

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}
    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
    \definecolor{ansi-default-inverse-bg}{HTML}{000000}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatibility definitions
    \def\gt{>}
    \def\lt{<}
    \let\Oldtex\TeX
    \let\Oldlatex\LaTeX
    \renewcommand{\TeX}{\textrm{\Oldtex}}
    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
    % Document parameters
    % Document title
    \title{2-factor-Hull-White\_model\_calibration}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % For linebreaks inside Verbatim environment from package fancyvrb. 
    \makeatletter
        \newbox\Wrappedcontinuationbox 
        \newbox\Wrappedvisiblespacebox 
        \newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}} 
        \newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}} 
        \newcommand*\Wrappedcontinuationindent {3ex } 
        \newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox} 
        % Take advantage of the already applied Pygments mark-up to insert 
        % potential linebreaks for TeX processing. 
        %        {, <, #, %, $, ' and ": go to next line. 
        %        _, }, ^, &, >, - and ~: stay at end of broken line. 
        % Use of \textquotesingle for straight quote. 
        \newcommand*\Wrappedbreaksatspecials {% 
            \def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}% 
            \def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}% 
            \def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}% 
            \def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}% 
            \def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}% 
            \def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}% 
            \def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}% 
            \def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}% 
            \def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}% 
            \def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}% 
            \def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}% 
            \def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}% 
            \def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}% 
            \def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}% 
        } 
        % Some characters . , ; ? ! / are not pygmentized. 
        % This macro makes them "active" and they will insert potential linebreaks 
        \newcommand*\Wrappedbreaksatpunct {% 
            \lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}% 
            \lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}% 
            \lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}% 
            \lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}% 
            \lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}% 
            \lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}% 
            \lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}% 
            \catcode`\.\active
            \catcode`\,\active 
            \catcode`\;\active
            \catcode`\:\active
            \catcode`\?\active
            \catcode`\!\active
            \catcode`\/\active 
            \lccode`\~`\~ 	
        }
    \makeatother

    \let\OriginalVerbatim=\Verbatim
    \makeatletter
    \renewcommand{\Verbatim}[1][1]{%
        %\parskip\z@skip
        \sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
        \sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
        \def\FancyVerbFormatLine ##1{\hsize\linewidth
            \vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
                \doublehyphendemerits\z@\finalhyphendemerits\z@
                \strut ##1\strut}%
        }%
        % If the linebreak is at a space, the latter will be displayed as visible
        % space at end of first line, and a continuation symbol starts next line.
        % Stretch/shrink are however usually zero for typewriter font.
        \def\FV@Space {%
            \nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
            \discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
            {\kern\fontdimen2\font}%
        }%

        % Allow breaks at special characters using \PYG... macros.
        \Wrappedbreaksatspecials
        % Breaks at punctuation characters . , ; ? ! and / need catcode=\active 	
        \OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
    }
    \makeatother

    % Exact colors from NB
    \definecolor{incolor}{HTML}{303F9F}
    \definecolor{outcolor}{HTML}{D84315}
    \definecolor{cellborder}{HTML}{CFCFCF}
    \definecolor{cellbackground}{HTML}{F7F7F7}

    % prompt
    \makeatletter
    \newcommand{\boxspacing}{\kern\kvtcb@left@rule\kern\kvtcb@boxsep}
    \makeatother
    \newcommand{\prompt}[4]{
        \ttfamily\llap{{\color{#2}[#3]:\hspace{3pt}#4}}\vspace{-\baselineskip}
    }

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\begin{document}

\nocite{*} % this command forces all references in template.bib to be printed in the bibliography

\title{Price a European Up-and-out Call Option}

\author{
  Ng, Joe Hoong\\
  \texttt{ng\_joehoong@hotmail.com}
  \and
  Nguyen, Dang Duy Nghia \\
  \texttt{nghia002@e.ntu.edu.sg}
   \and
  Ansari, Zain Us Sami Ahmed \\
  \texttt{zainussami@gmail.com}  
   \and
   Thorne, Dylan \\
  \texttt{dylan.thorne@gmail.com}  
  }

\date{April. 8, 2020} % if this is omitted, the current date is used for the title page
\maketitle

\noindent
\textbf{Keywords:} Exotic Options, European up-and-out call option,  Black-Scholes-Merton model and Geometric Brownian Motion.

% the following creates an abstract -- it can be omitted
% an example of an environment: these have the form \begin{name} ... \end{name}
\begin{abstract}
In this report we discuss European up-and-out call option.  In the first section we introduce a European up-and-out call option, in the second section we simulate paths for the underlying share and for the counterparty's firm value using varying sample sizes , in the third section we Determine Monte Carlo estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA),  in the fourth section we calculate the Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA. We conclude the report by discussing ....................  
\end{abstract}

\section{Introduction
}
The pricing calculations in this paper concern a European up-and-out call option. The up-and-out option is a type barrier option that is worthless if the barrier price is reached or exceeded, but otherwise behaves exactly as a standard European call option. There are four main variants of barrier options, two of which are cancelled by reaching the barrier price (up-and-out and down-and-out) and two of which are only valid if the barrier is reached (up-and-in and down-and-in).

The standard European call option payoff formula can be applied with the addition of a check to determine if the barrier price was reached or exceeded, in which case the payoff is zero for the up-and-out option. The same approach could be applied with minor adjustments to price down-and-out, down-and-in or up-and-in barrier options.

Possible paths for the up-and-out barrier option payoff would look similar to the chart below, where two of the paths have crossed the barrier and resulted in zero payoff, but the other three have not crossed the barrier and behave like a vanilla option.

\begin{figure}
    \centering
    \caption{Simulated Payoffs for an Up-and-out Barrier Option}
    \includegraphics{images/barrier-example.png}
\end{figure}

\section{Simulated Paths for the Underlying Share and Counterparty Firm
}

 In order to simulate paths for the underlying share and the firm, a matrix of correlated prices is generated based on the requirement for a correlation of 0.2.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}

    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
\end{Verbatim}
\end{tcolorbox}

A Pearson test can be used to verify that the correlation is very close to the 0.2 target value. In Python this can be achieved as follows.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{5}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}

\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}

\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n+nb}{print}\PY{p}{(}\PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
(0.2035028479587627, 6.07336614624919e-186)
(0.1986599648970965, 4.04999708397334e-177)
(0.2016759847597355, 1.3775160789695309e-182)
(0.20364055709605317, 3.381815103189066e-186)
(0.19385401550478024, 1.3726860317349184e-168)
(0.19892212605701942, 1.3666646645127986e-177)
(0.18344242259502544, 7.064732561303709e-151)
(0.20519864966486748, 4.356484560250648e-189)
(0.193927020114363, 1.022531700201078e-168)
(0.19751037260327703, 4.659785935918803e-175)
(0.20393895669991588, 9.495454795149592e-187)
(0.20458792743312265, 5.953557128978809e-188)
(0.2042028358117276, 3.0829601588859696e-187)
(0.19512700379639908, 7.943982338391081e-171)
(0.19603082201925184, 2.003660281095667e-172)
(0.19820752618175266, 2.630853001655849e-176)
(0.20299979761482267, 5.137198920374959e-185)
(0.1966663418793928, 1.4903037901828931e-173)
(0.20319824398313788, 2.214204369119104e-185)
(0.20765530182748704, 1.0810080941108714e-193)
    \end{Verbatim}

The payoff calculation for the up-and-out barrier option is defined as follows.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}

\PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

The simulated payoff paths over twelve months are plotted below, with an arbitrary starting value of 200 for the firm value.

\begin{figure}
    \centering
    \caption{Simulated Payoff Paths over 12 Months}
    \includegraphics{images/all-paths.png}
\end{figure}

\section{Monte Carlo Estimations
}

\subsection{Default-Free Value Estimation}
\begin{figure}
    \centering
    \caption{Simulated Payoff Paths over 12 Months}
    \includegraphics{images/default-free.png}
\end{figure}

\subsection{Credit Valuation Adjustment Estimation}

\section{Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA.}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{1}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{QuantLib} \PY{k}{as} \PY{n+nn}{ql}
\PY{k+kn}{from} \PY{n+nn}{collections} \PY{k+kn}{import} \PY{n}{namedtuple}
\PY{k+kn}{import} \PY{n+nn}{math}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{today} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Date}\PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{n}{ql}\PY{o}{.}\PY{n}{February}\PY{p}{,} \PY{l+m+mi}{2020}\PY{p}{)}\PY{p}{;}
\PY{n}{settlement}\PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Date}\PY{p}{(}\PY{l+m+mi}{19}\PY{p}{,} \PY{n}{ql}\PY{o}{.}\PY{n}{February}\PY{p}{,} \PY{l+m+mi}{2020}\PY{p}{)}\PY{p}{;}
\PY{n}{ql}\PY{o}{.}\PY{n}{Settings}\PY{o}{.}\PY{n}{instance}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{evaluationDate} \PY{o}{=} \PY{n}{today}\PY{p}{;}
\PY{n}{term\PYZus{}structure} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{YieldTermStructureHandle}\PY{p}{(}
    \PY{n}{ql}\PY{o}{.}\PY{n}{FlatForward}\PY{p}{(}\PY{n}{settlement}\PY{p}{,}\PY{l+m+mf}{0.04875825}\PY{p}{,}\PY{n}{ql}\PY{o}{.}\PY{n}{Actual365Fixed}\PY{p}{(}\PY{p}{)}\PY{p}{)}
    \PY{p}{)}
\PY{n}{index} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Euribor1Y}\PY{p}{(}\PY{n}{term\PYZus{}structure}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
--------------------------------------------------------------------------------
--
    Model Price    Market Price     Implied Vol      Market Vol       Rel Error
--------------------------------------------------------------------------------
--
        0.00871         0.00949         0.10531         0.11480        -0.08263
        0.00968         0.01008         0.10634         0.11080        -0.04018
        0.00867         0.00871         0.10652         0.10700        -0.00448
        0.00653         0.00625         0.10665         0.10210         0.04442
        0.00357         0.00334         0.10680         0.10000         0.06773
--------------------------------------------------------------------------------
--
Cumulative Error :         0.12288
    \end{Verbatim}

\section{Conclusion}

\newpage
\section*{} \label{bibsection}

% the second parameter MMMMM should be as long as the longest label you use, in my case Smoller -- if you use % numbers only, use 99
% use \cite{refname} to refer to bibliography item \bibitem{refname} 
% LaTeX assigns a number, unless you use \bibitem[Name]{refname} -- in this case
% LaTeX prints Name when you use \cite{refname}
\begin{thebibliography}{MMMMM} 
\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Insitute of Technology (2014).

\end{thebibliography}
\bibliographystyle{plain}
\bibliography{template}

\end{document}

### 2020-04-09 Submission1.tex
Added CVA, fixed typo

@@
 \begin{abstract}
-In this report we discuss European up-and-out call option.
-In the first section we introduce a European up-and-out call option, in the second section we simulate paths for the underlying share and for the counterparty's firm value using varying sample sizes , in the third section we Determine Monte Carlo estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA),  in the fourth section we calculate the Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA.
-We conclude the report by discussing ....................
+This report presents the results of the simulation of a European up-and-out call option over twelve months.
+The Black-Scholes-Merton model will be used to implement Monte Carlo estimations using Python code.
+The estimations will simulate paths for the underlying share and the counterparty's firm value using varying sample sizes, and determine estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA).
+Following from these it is simple to price the option incorporating counterparty risk, given by the default-free price less the CVA.
 \end{abstract}
@@
 \subsection{Credit Valuation Adjustment Estimation}
+\begin{figure}
+    \centering
+    \caption{Simulated Payoff Paths over 12 Months}
+    \includegraphics{images/cva.png}
+\end{figure}
 
-\section{Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA.}
+\section{Incorporating Counterparty Risk}
+
+To estimate the price of the option incorporating counterparty risk, the CVA is subtracted from the default-free price; both of these have already been calculated at this point.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{20}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
+    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+
+    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
+    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+
+    \PY{n}{option\PYZus{}cva\PYZus{}price} \PY{o}{=} \PY{n}{option\PYZus{}price} \PY{o}{\PYZhy{}} \PY{n}{amount\PYZus{}lost}
+
+    \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+\begin{figure}
+    \centering
+    \caption{Simulated Payoff Paths over 12 Months}
+    \includegraphics{images/with-counterparty-risk.png}
+\end{figure}
 
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Insitute of Technology (2014).
+\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Institute of Technology (2014).
 

### 2020-04-09 Submission1.tex
Introduction finished

--- 2020-04-09 Submission1.tex
@@
     \fi
-
-    \usepackage{graphicx} %package to manage images
-    \graphicspath{ {./images/} }
-    \usepackage{wrapfig}
 
@@
 }
-The pricing calculations in this paper concern a European up-and-out call option.
-The up-and-out option is a type barrier option that is worthless if the barrier price is reached or exceeded, but otherwise behaves exactly as a standard European call option.
-There are four main variants of barrier options, two of which are cancelled by reaching the barrier price (up-and-out and down-and-out) and two of which are only valid if the barrier is reached (up-and-in and down-and-in).
+A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.
+The payoff of an up-and-out option at maturity $T$ is given by,
 
-The standard European call option payoff formula can be applied with the addition of a check to determine if the barrier price was reached or exceeded, in which case the payoff is zero for the up-and-out option.
-The same approach could be applied with minor adjustments to price down-and-out, down-and-in or up-and-in barrier options.
+\[
+Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
+\]
+Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.
+This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level.
+\\
 
-Possible paths for the up-and-out barrier option payoff would look similar to the chart below, where two of the paths have crossed the barrier and resulted in zero payoff, but the other three have not crossed the barrier and behave like a vanilla option.
+The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.
+This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}.
+Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.
 
-\begin{figure}
-    \centering
-    \caption{Simulated Payoffs for an Up-and-out Barrier Option}
-    \includegraphics{images/barrier-example.png}
-\end{figure}
-
-\section{Simulated Paths for the Underlying Share and Counterparty Firm
+\section{Lifetime simulations of the option. 
 }
-
- In order to simulate paths for the underlying share and the firm, a matrix of correlated prices is generated based on the requirement for a correlation of 0.2.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{4}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
-    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
-    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}
-
-    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
-    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
-    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
-    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
-    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
-\end{Verbatim}
-\end{tcolorbox}
-
-A Pearson test can be used to verify that the correlation is very close to the 0.2 target value. In Python this can be achieved as follows.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{5}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
-\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
-\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}
-
-\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
-
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n+nb}{print}\PY{p}{(}\PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-(0.2035028479587627, 6.07336614624919e-186)
-(0.1986599648970965, 4.04999708397334e-177)
-(0.2016759847597355, 1.3775160789695309e-182)
-(0.20364055709605317, 3.381815103189066e-186)
-(0.19385401550478024, 1.3726860317349184e-168)
-(0.19892212605701942, 1.3666646645127986e-177)
-(0.18344242259502544, 7.064732561303709e-151)
-(0.20519864966486748, 4.356484560250648e-189)
-(0.193927020114363, 1.022531700201078e-168)
-(0.19751037260327703, 4.659785935918803e-175)
-(0.20393895669991588, 9.495454795149592e-187)
-(0.20458792743312265, 5.953557128978809e-188)
-(0.2042028358117276, 3.0829601588859696e-187)
-(0.19512700379639908, 7.943982338391081e-171)
-(0.19603082201925184, 2.003660281095667e-172)
-(0.19820752618175266, 2.630853001655849e-176)
-(0.20299979761482267, 5.137198920374959e-185)
-(0.1966663418793928, 1.4903037901828931e-173)
-(0.20319824398313788, 2.214204369119104e-185)
-(0.20765530182748704, 1.0810080941108714e-193)
-    \end{Verbatim}
-
-The payoff calculation for the up-and-out barrier option is defined as follows.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{11}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
-\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
-    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
-    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
-
-\PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-The simulated payoff paths over twelve months are plotted below, with an arbitrary starting value of 200 for the firm value.
-
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/all-paths.png}
-\end{figure}
-
-\section{Monte Carlo Estimations
+\section{Monte Carlo estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA).
 }
-
-\subsection{Default-Free Value Estimation}
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/default-free.png}
-\end{figure}
-
-\subsection{Credit Valuation Adjustment Estimation}
 
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Insitute of Technology (2014).
+\bibitem{Merton1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
+\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
+\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
+\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
+\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
 

### 2020-04-09 Submission1.tex
Revert "Introduction finished"
This reverts commit dc1bd7bc7a046f54a520e7602528b34b36e9e2ac.

@@
 }
-A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.
-The payoff of an up-and-out option at maturity $T$ is given by,
-
-\[
-Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
-\]
-Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.
-This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level.
-\\
-
-The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.
-This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}.
-Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.
 
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{Merton1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
-\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
-\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
-\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
-\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
+\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Insitute of Technology (2014).
 

### 2020-04-09 Submission1.tex
Intro Revised

--- 2020-04-09 Submission1.tex
@@
 }
-The pricing calculations in this paper concern a European up-and-out call option.
-The up-and-out option is a type barrier option that is worthless if the barrier price is reached or exceeded, but otherwise behaves exactly as a standard European call option.
-There are four main variants of barrier options, two of which are cancelled by reaching the barrier price (up-and-out and down-and-out) and two of which are only valid if the barrier is reached (up-and-in and down-and-in).
+A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.
+The payoff of an up-and-out option at maturity $T$ is given by,
 
-The standard European call option payoff formula can be applied with the addition of a check to determine if the barrier price was reached or exceeded, in which case the payoff is zero for the up-and-out option.
-The same approach could be applied with minor adjustments to price down-and-out, down-and-in or up-and-in barrier options.
+\[
+Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
+\]
+Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.
+This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level.
+\\
+
+The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.
+This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}.
+Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.
 
@@
     \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
-
 \PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
@@
     \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
     \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
     \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
     \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
@@
 \PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}
-
 \PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
-
 \PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
@@
     \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
-
 \PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
@@
 \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-
 \PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
@@
     \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
-
     \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Institute of Technology (2014).
+\bibitem{Merton1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
+\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
+\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
+\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
+\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
 

### 2020-04-12 Submission1.tex
Cleanup and Compilation

@@
 
+We initialize most variables as given by the question. We assume the
+counterparty firm's value is at 200, as this is above the counterparty's
+debt due in one year. Also, we calculate the default-free value of our
+option to be 6.60, so we select a firm value not too distant such that
+the CVA value we calculate is not negligible. For example, if we chose
+counterparty firm value as 1,000, the CVA would be 0.000.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{2}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{} Initialize problem parameters}
+\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1} \PY{c+c1}{\PYZsh{} option maturity}
+\PY{n}{L} \PY{o}{=} \PY{l+m+mi}{150} \PY{c+c1}{\PYZsh{} up\PYZhy{}and\PYZhy{}out barrier}
+\PY{n}{S0} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} current share price}
+\PY{n}{K} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} strike price, at\PYZhy{}the\PYZhy{}money}
+\PY{n}{risk\PYZus{}free} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{08} \PY{c+c1}{\PYZsh{} risk\PYZhy{}free rate}
+\PY{n}{sigma} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{3} \PY{c+c1}{\PYZsh{} volatility}
+\PY{n}{v\PYZus{}0} \PY{o}{=} \PY{l+m+mi}{200} \PY{c+c1}{\PYZsh{} counterparty firm current value (Our assumption) }
+\PY{n}{sigma\PYZus{}firm} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{25} \PY{c+c1}{\PYZsh{} volatility for the counterparty\PYZsq{}s firm}
+\PY{n}{debt} \PY{o}{=} \PY{l+m+mi}{175} \PY{c+c1}{\PYZsh{} counterparty\PYZsq{}s debt, due in one year }
+\PY{n}{corr} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{2} \PY{c+c1}{\PYZsh{} correlation}
+\PY{n}{recovery\PYZus{}rate} \PY{o}{=} \PY{l+m+mf}{0.25} \PY{c+c1}{\PYZsh{} recovery rate}
+\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}}
+\PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
+\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
 \section{Simulated Paths for the Underlying Share and Counterparty Firm
@@
 
- In order to simulate paths for the underlying share and the firm, a matrix of correlated prices is generated based on the requirement for a correlation of 0.2.
+ In order to simulate paths for the underlying share and the firm,  we use a Cholesky decomposition to generate the correlated price paths.
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{4}{\boxspacing}
+\prompt{In}{incolor}{3}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
@@
     \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
+
 \PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
@@
     \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+
     \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
     \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+
     \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
@@
 
-A Pearson test can be used to verify that the correlation is very close to the 0.2 target value. In Python this can be achieved as follows.
+    To double check that the stock prices and firm values monthly returns
+are correlated, we check them as follows, generating 20 different price
+paths with 10,000 timesteps.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{4}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
+\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
+\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{10000}\PY{p}{)}
+
+\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
+
+\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
+    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
+    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
+    \PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Pearson correlation coefficient : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{, Two\PYZhy{}tailed p\PYZhy{}value }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.198, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.184, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.203, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.204, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.209, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.198, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.215, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.187, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.192, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.186, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.204, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.205, Two-tailed p-value 0.000
+Pearson correlation coefficient : 0.188, Two-tailed p-value 0.000
+    \end{Verbatim}
+
+    Let's try to simulate the share price with a small number of sample
+paths and visualize them over the course of 12 months
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
-\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
-\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}
-\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n+nb}{print}\PY{p}{(}\PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
+\PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{5}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}
+\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
+\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Share price over 12 months}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
 \end{Verbatim}
@@
 
-    \begin{Verbatim}[commandchars=\\\{\}]
-(0.2035028479587627, 6.07336614624919e-186)
-(0.1986599648970965, 4.04999708397334e-177)
-(0.2016759847597355, 1.3775160789695309e-182)
-(0.20364055709605317, 3.381815103189066e-186)
-(0.19385401550478024, 1.3726860317349184e-168)
-(0.19892212605701942, 1.3666646645127986e-177)
-(0.18344242259502544, 7.064732561303709e-151)
-(0.20519864966486748, 4.356484560250648e-189)
-(0.193927020114363, 1.022531700201078e-168)
-(0.19751037260327703, 4.659785935918803e-175)
-(0.20393895669991588, 9.495454795149592e-187)
-(0.20458792743312265, 5.953557128978809e-188)
-(0.2042028358117276, 3.0829601588859696e-187)
-(0.19512700379639908, 7.943982338391081e-171)
-(0.19603082201925184, 2.003660281095667e-172)
-(0.19820752618175266, 2.630853001655849e-176)
-(0.20299979761482267, 5.137198920374959e-185)
-(0.1966663418793928, 1.4903037901828931e-173)
-(0.20319824398313788, 2.214204369119104e-185)
-(0.20765530182748704, 1.0810080941108714e-193)
-    \end{Verbatim}
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_10_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 
-The payoff calculation for the up-and-out barrier option is defined as follows.
+    We can do the same thing to simulate counterparty firm's value
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{11}{\boxspacing}
+\prompt{In}{incolor}{6}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{firm\PYZus{}value\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
+\PY{n}{firm\PYZus{}value\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Counterparty firm}\PY{l+s+s2}{\PYZsq{}}\PY{l+s+s2}{s value over 12 months}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_12_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+     Let's visualize when the stopped process is appied
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{8}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{stop}\PY{p}{(}\PY{n}{s}\PY{p}{,} \PY{n}{cond}\PY{p}{)}\PY{p}{:}
+    \PY{n}{ret} \PY{o}{=} \PY{n}{s}\PY{o}{.}\PY{n}{copy}\PY{p}{(}\PY{p}{)}
+    \PY{n}{r} \PY{o}{=} \PY{n}{ret}\PY{p}{[}\PY{n}{cond}\PY{p}{]}
+    \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{r}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{:}
+        \PY{n+nb}{print}\PY{p}{(}\PY{n}{r}\PY{p}{)}
+        \PY{n}{ret}\PY{p}{[}\PY{n}{r}\PY{o}{.}\PY{n}{idxmin}\PY{p}{(}\PY{p}{)}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{l+m+mi}{0}
+    \PY{k}{return} \PY{n}{ret}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{9}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{apply}\PY{p}{(}\PY{k}{lambda} \PY{n}{s}\PY{p}{:} \PY{n}{stop}\PY{p}{(}\PY{n}{s}\PY{p}{,} \PY{n}{s}\PY{o}{\PYZgt{}}\PY{n}{L}\PY{p}{)}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_17_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+    We then define a function to calculate the payoff for the up-and-out call option.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{10}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
@@
     \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
+
 \PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
@@
 
-The simulated payoff paths over twelve months are plotted below, with an arbitrary starting value of 200 for the firm value.
+            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
+\prompt{Out}{outcolor}{10}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+array([ 0.        , 37.34484527, 43.05073004,  0.        ,  7.00008561])
+\end{Verbatim}
+\end{tcolorbox}
+We now create the share and firm price paths for sample sizes 1000, 2000, \ldots{}., 50000, as required for part 1 of the assignment.
 
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/all-paths.png}
-\end{figure}
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{11}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+\PY{n}{firm\PYZus{}val\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+
+\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
+
+\PY{k}{for} \PY{n}{sample\PYZus{}size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
+    \PY{n}{share\PYZus{}val}\PY{p}{,} \PY{n}{firm\PYZus{}val} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}
+
+    \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{share\PYZus{}val}
+    \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{firm\PYZus{}val}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We now plot the share and firm price paths for sample size of 1000.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{12}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_23_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{13}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_24_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 
@@
 \subsection{Default-Free Value Estimation}
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/default-free.png}
-\end{figure}
+To calculate Monte Carlo estimate of the default-free option value, we
+calculate the average payoff of the 1000s of sample price paths, to
+estimate the price of the option
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{14}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{} Estimate the default\PYZhy{}free value of the option:}
+\PY{n}{option\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{option\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
+    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+    \PY{n}{option\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n}{option\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    Prices of default-free option at various sample sizes:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{15}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{option\PYZus{}estimate}\PY{p}{)}\PY{p}{)}\PY{p}{:}
+    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, Option value: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{option\PYZus{}estimate}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+sample size: 1000, Option value: 6.853
+sample size: 2000, Option value: 6.826
+sample size: 3000, Option value: 6.831
+sample size: 4000, Option value: 6.739
+sample size: 5000, Option value: 6.551
+sample size: 6000, Option value: 6.871
+sample size: 7000, Option value: 6.713
+sample size: 8000, Option value: 7.028
+sample size: 9000, Option value: 6.412
+sample size: 10000, Option value: 6.810
+sample size: 11000, Option value: 6.831
+sample size: 12000, Option value: 6.704
+sample size: 13000, Option value: 6.682
+sample size: 14000, Option value: 6.760
+sample size: 15000, Option value: 6.619
+sample size: 16000, Option value: 6.693
+sample size: 17000, Option value: 6.694
+sample size: 18000, Option value: 6.678
+sample size: 19000, Option value: 6.580
+sample size: 20000, Option value: 6.678
+sample size: 21000, Option value: 6.726
+sample size: 22000, Option value: 6.587
+sample size: 23000, Option value: 6.754
+sample size: 24000, Option value: 6.784
+sample size: 25000, Option value: 6.670
+sample size: 26000, Option value: 6.656
+sample size: 27000, Option value: 6.713
+sample size: 28000, Option value: 6.706
+sample size: 29000, Option value: 6.748
+sample size: 30000, Option value: 6.612
+sample size: 31000, Option value: 6.620
+sample size: 32000, Option value: 6.870
+sample size: 33000, Option value: 6.738
+sample size: 34000, Option value: 6.744
+sample size: 35000, Option value: 6.683
+sample size: 36000, Option value: 6.700
+sample size: 37000, Option value: 6.672
+sample size: 38000, Option value: 6.694
+sample size: 39000, Option value: 6.678
+sample size: 40000, Option value: 6.676
+sample size: 41000, Option value: 6.781
+sample size: 42000, Option value: 6.623
+sample size: 43000, Option value: 6.614
+sample size: 44000, Option value: 6.674
+sample size: 45000, Option value: 6.676
+sample size: 46000, Option value: 6.740
+sample size: 47000, Option value: 6.732
+sample size: 48000, Option value: 6.706
+sample size: 49000, Option value: 6.649
+sample size: 50000, Option value: 6.628
+    \end{Verbatim}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{16}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_30_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 
 \subsection{Credit Valuation Adjustment Estimation}
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/cva.png}
-\end{figure}
 
-\section{Incorporating Counterparty Risk}
+To calculate Monte Carlo estimate of the credit value adjustment, we
+calculate the average loss of the 1000s of sample price paths, which
+happens when we both see a gain in the option with hold and when the
+counterparty firm value is less than its debt.
 
-To estimate the price of the option incorporating counterparty risk, the CVA is subtracted from the default-free price; both of these have already been calculated at this point.
+As per notes, we assume that default can only occur at time T, and firm
+defaults if the firm value is below firm debt amount
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{17}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{terminal\PYZus{}value}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{T}\PY{p}{)}\PY{p}{:} \PY{c+c1}{\PYZsh{}applies to both firm and stock}
+    \PY{k}{return} \PY{n}{S\PYZus{}0} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{*} \PY{n}{T} \PY{o}{+} \PY{n}{sigma} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)} \PY{o}{*} \PY{n}{Z}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{18}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{cva\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{cva\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
+    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
+    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+    \PY{n}{cva\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n}{cva\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
+
+\end{Verbatim}
+\end{tcolorbox}
+
+    Credit value adjustment at various sample sizes:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{19}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{cva\PYZus{}estimate}\PY{p}{)}\PY{p}{)}\PY{p}{:}
+    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, CVA: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{cva\PYZus{}estimate}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Sample size: 1000, CVA: 0.856
+Sample size: 2000, CVA: 0.906
+Sample size: 3000, CVA: 0.974
+Sample size: 4000, CVA: 0.977
+Sample size: 5000, CVA: 0.908
+Sample size: 6000, CVA: 0.957
+Sample size: 7000, CVA: 0.953
+Sample size: 8000, CVA: 1.035
+Sample size: 9000, CVA: 0.923
+Sample size: 10000, CVA: 0.977
+Sample size: 11000, CVA: 0.937
+Sample size: 12000, CVA: 0.977
+Sample size: 13000, CVA: 0.968
+Sample size: 14000, CVA: 0.947
+Sample size: 15000, CVA: 1.021
+Sample size: 16000, CVA: 0.948
+Sample size: 17000, CVA: 0.906
+Sample size: 18000, CVA: 0.918
+Sample size: 19000, CVA: 0.960
+Sample size: 20000, CVA: 0.958
+Sample size: 21000, CVA: 0.937
+Sample size: 22000, CVA: 0.928
+Sample size: 23000, CVA: 0.951
+Sample size: 24000, CVA: 1.024
+Sample size: 25000, CVA: 0.931
+Sample size: 26000, CVA: 0.905
+Sample size: 27000, CVA: 0.913
+Sample size: 28000, CVA: 0.966
+Sample size: 29000, CVA: 0.933
+Sample size: 30000, CVA: 0.917
+Sample size: 31000, CVA: 0.941
+Sample size: 32000, CVA: 1.025
+Sample size: 33000, CVA: 0.929
+Sample size: 34000, CVA: 0.982
+Sample size: 35000, CVA: 0.973
+Sample size: 36000, CVA: 0.944
+Sample size: 37000, CVA: 0.980
+Sample size: 38000, CVA: 0.934
+Sample size: 39000, CVA: 0.928
+Sample size: 40000, CVA: 0.950
+Sample size: 41000, CVA: 0.928
+Sample size: 42000, CVA: 0.916
+Sample size: 43000, CVA: 0.941
+Sample size: 44000, CVA: 0.951
+Sample size: 45000, CVA: 0.944
+Sample size: 46000, CVA: 0.947
+Sample size: 47000, CVA: 0.943
+Sample size: 48000, CVA: 0.954
+Sample size: 49000, CVA: 0.959
+Sample size: 50000, CVA: 0.931
+    \end{Verbatim}
 
@@
 \begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{cva\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{cva\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_36_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+\section{Incorporating Counterparty Risk}
+
+We calculate the Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA.
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{21}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
 \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
 \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
 \PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
@@
     \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+
     \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
@@
 
-\begin{figure}
-    \centering
-    \caption{Simulated Payoff Paths over 12 Months}
-    \includegraphics{images/with-counterparty-risk.png}
-\end{figure}
+    Credit value adjustment at various sample sizes:
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{1}{\boxspacing}
+\prompt{In}{incolor}{22}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{k+kn}{import} \PY{n+nn}{QuantLib} \PY{k}{as} \PY{n+nn}{ql}
-\PY{k+kn}{from} \PY{n+nn}{collections} \PY{k+kn}{import} \PY{n}{namedtuple}
-\PY{k+kn}{import} \PY{n+nn}{math}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{2}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{today} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Date}\PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{n}{ql}\PY{o}{.}\PY{n}{February}\PY{p}{,} \PY{l+m+mi}{2020}\PY{p}{)}\PY{p}{;}
-\PY{n}{settlement}\PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Date}\PY{p}{(}\PY{l+m+mi}{19}\PY{p}{,} \PY{n}{ql}\PY{o}{.}\PY{n}{February}\PY{p}{,} \PY{l+m+mi}{2020}\PY{p}{)}\PY{p}{;}
-\PY{n}{ql}\PY{o}{.}\PY{n}{Settings}\PY{o}{.}\PY{n}{instance}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{evaluationDate} \PY{o}{=} \PY{n}{today}\PY{p}{;}
-\PY{n}{term\PYZus{}structure} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{YieldTermStructureHandle}\PY{p}{(}
-    \PY{n}{ql}\PY{o}{.}\PY{n}{FlatForward}\PY{p}{(}\PY{n}{settlement}\PY{p}{,}\PY{l+m+mf}{0.04875825}\PY{p}{,}\PY{n}{ql}\PY{o}{.}\PY{n}{Actual365Fixed}\PY{p}{(}\PY{p}{)}\PY{p}{)}
-    \PY{p}{)}
-\PY{n}{index} \PY{o}{=} \PY{n}{ql}\PY{o}{.}\PY{n}{Euribor1Y}\PY{p}{(}\PY{n}{term\PYZus{}structure}\PY{p}{)}
+\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{)}\PY{p}{)}\PY{p}{:}
+    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, CVA\PYZhy{}adjusted option value: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
 \end{Verbatim}
@@
     \begin{Verbatim}[commandchars=\\\{\}]
---------------------------------------------------------------------------------
---
-    Model Price    Market Price     Implied Vol      Market Vol       Rel Error
---------------------------------------------------------------------------------
---
-        0.00871         0.00949         0.10531         0.11480        -0.08263
-        0.00968         0.01008         0.10634         0.11080        -0.04018
-        0.00867         0.00871         0.10652         0.10700        -0.00448
-        0.00653         0.00625         0.10665         0.10210         0.04442
-        0.00357         0.00334         0.10680         0.10000         0.06773
---------------------------------------------------------------------------------
---
-Cumulative Error :         0.12288
+Sample size: 1000, CVA-adjusted option value: 5.997
+Sample size: 2000, CVA-adjusted option value: 5.920
+Sample size: 3000, CVA-adjusted option value: 5.857
+Sample size: 4000, CVA-adjusted option value: 5.763
+Sample size: 5000, CVA-adjusted option value: 5.643
+Sample size: 6000, CVA-adjusted option value: 5.913
+Sample size: 7000, CVA-adjusted option value: 5.760
+Sample size: 8000, CVA-adjusted option value: 5.993
+Sample size: 9000, CVA-adjusted option value: 5.490
+Sample size: 10000, CVA-adjusted option value: 5.834
+Sample size: 11000, CVA-adjusted option value: 5.894
+Sample size: 12000, CVA-adjusted option value: 5.726
+Sample size: 13000, CVA-adjusted option value: 5.715
+Sample size: 14000, CVA-adjusted option value: 5.814
+Sample size: 15000, CVA-adjusted option value: 5.597
+Sample size: 16000, CVA-adjusted option value: 5.745
+Sample size: 17000, CVA-adjusted option value: 5.788
+Sample size: 18000, CVA-adjusted option value: 5.760
+Sample size: 19000, CVA-adjusted option value: 5.620
+Sample size: 20000, CVA-adjusted option value: 5.720
+Sample size: 21000, CVA-adjusted option value: 5.788
+Sample size: 22000, CVA-adjusted option value: 5.659
+Sample size: 23000, CVA-adjusted option value: 5.803
+Sample size: 24000, CVA-adjusted option value: 5.760
+Sample size: 25000, CVA-adjusted option value: 5.739
+Sample size: 26000, CVA-adjusted option value: 5.751
+Sample size: 27000, CVA-adjusted option value: 5.799
+Sample size: 28000, CVA-adjusted option value: 5.740
+Sample size: 29000, CVA-adjusted option value: 5.815
+Sample size: 30000, CVA-adjusted option value: 5.695
+Sample size: 31000, CVA-adjusted option value: 5.678
+Sample size: 32000, CVA-adjusted option value: 5.845
+Sample size: 33000, CVA-adjusted option value: 5.809
+Sample size: 34000, CVA-adjusted option value: 5.762
+Sample size: 35000, CVA-adjusted option value: 5.709
+Sample size: 36000, CVA-adjusted option value: 5.756
+Sample size: 37000, CVA-adjusted option value: 5.693
+Sample size: 38000, CVA-adjusted option value: 5.760
+Sample size: 39000, CVA-adjusted option value: 5.750
+Sample size: 40000, CVA-adjusted option value: 5.726
+Sample size: 41000, CVA-adjusted option value: 5.853
+Sample size: 42000, CVA-adjusted option value: 5.707
+Sample size: 43000, CVA-adjusted option value: 5.673
+Sample size: 44000, CVA-adjusted option value: 5.724
+Sample size: 45000, CVA-adjusted option value: 5.732
+Sample size: 46000, CVA-adjusted option value: 5.793
+Sample size: 47000, CVA-adjusted option value: 5.789
+Sample size: 48000, CVA-adjusted option value: 5.753
+Sample size: 49000, CVA-adjusted option value: 5.689
+Sample size: 50000, CVA-adjusted option value: 5.697
     \end{Verbatim}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{23}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA\PYZhy{}adjusted option prices estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 

### 2020-04-12 Submission1.tex
Added Conclusion

@@
     { \hspace*{\fill} \\}
-
 \section{Conclusion}
+We are well aware that Black-Scholes formula was derived under assumptions which might not hold in a real market, as an example, if the share price deviates from the geometric Brownian motion, then our estimates can be wrong by a big margin.
+However with the assumptions of Black-Scholes-Merton model we were able to price a European Up-and-out Call Option.
+We were able to use knowledge from module 2 and 3 to generate Python code for monthly simulations for the lifetime of the option.
+Also, our Monte Carlo estimates are highly dependant on parameters such as firm value if firm value is well above debt value and the volatility of the firm is low, the chance of default is really low.
 

### 2020-04-13 Report.tex
fix typo

--- 2020-04-12 Submission1.tex
@@
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Counterparty firm value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
 \end{Verbatim}
@@
 
-    Credit value adjustment at various sample sizes:
+    Credit value adjusted option values at various sample sizes:
 

### 2020-04-26 week5/main.tex
Added report draft and plot legends

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage[backend=biber]{biblatex}
\addbibresource{main.bib}
\setlength{\parindent}{0pt}
\usepackage[Export]{adjustbox} % Used to constrain images to a maximum size
\adjustboxset{max size={0.9\linewidth}{0.9\paperheight}}

\title{Computational Finance Submission 2: \\A Vanilla European Call Option with Stochastic Volatility}
\author{Joe Hoong Ng (ng\_joehoong@hotmail.com)
\\Dang Duy Nghia Nguyen (nghia002@e.ntu.edu.sg)
\\Dylan Thorne (dylan.thorne@gmail.com)
\\Zain Us Sami Ahmed Ansari (zainussami@gmail.com)}

\date{April 2020}

\begin{document}

\maketitle

\begin{abstract}
    In this paper, we price a vanilla European call option under the Heston model and then simulate the monthly share price over a year using the Constant Elasticity of Variance (CEV) model, with the assumption of constant volatility each month. Monte Carlo simulations with varying sample sizes are run and the results are plotted against the closed form value for comparison.
\end{abstract}

\section{Part 1: Option Price Estimation}

In the first submission, the parameters for the option were supplied as follows:
\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The up-and-out barrier for the option is \$150
    \item The current share price is \$100
    \item The risk-free continuously compounded interest rate is 8%
    \item The volatility for the underlying share is 30%
    \item The volatility for the counterparty’s firm value is 25%
    \item The counterparty’s debt, due in one year, is \$175
    \item The correlation between the counterparty and the stock is constant at 0.2
    \item The recovery rate with the counterparty is 25%.
\end{itemize}

With the assumption that the underlying share follows the Heston model dynamics, the additional parameters required are specified as follows:
\begin{itemize}
    \item $\nu_0 = 0.06$
    \item $\kappa = 9$
    \item $\theta = 0.06$
    \item $\rho = −0.4$
\end{itemize}

The characteristic function is implemented using a function presented by Albrecher et al \cite{hestontrap}. The function is written as:
\[\phi_{S_T} = exp(C(\tau;u)+D(\tau;u)v_t + iu \log(S_t) )\]

Where,

\[C(\tau;u) = ri\tau u + \theta \kappa [\tau x\_ - \frac{1}{a}\log(\frac{1-ge^{d\tau}}{1-g})],\]

\[D(\tau;u) = (\frac{1-e^{d\tau}}{1-ge^{d\tau}})x\_,\]

\[\tau = T -t ,\]

\[ g = \frac{x\_}{x_+},\]

\[ x_\pm = \frac{b\pm d}{2a},\]

\[ d = \sqrt{b^2 - 4ac},\]

\[ c = - \frac{u^2 + Ui}{2},\]

\[ b = \kappa - \rho \sigma iu,\]

\[ a = \frac {\sigma^2}{2}\]

This formula is implemented in Python code and the resulting estimate for the vanilla European call option price is approximately \$13.735.

\section{Part 2: Underlying Share Price Path}

The underlying share price is estimated across a range of 50 different samples sizes ranging from 1000 to 50000 samples. The implementation is done using the CEV model and a function that iterates through the months, using the previous month's share price as an input parameter. A flag was also added to allow comparison between simulations using the CEV and Black-Scholes (BS) models.

\begin{center}
\adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_15_0.png}
\end{center}

\begin{center}
\adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_21_0.png}
\end{center}

The plot sample paths qualitatively validates that the algorithm is behaving as expected, diverging over time and grouping together with the majority of paths close to the mean value.

\section{Part 3: Monte Carlo Share Price Estimation}

The Monte Carlo price estimate for the vanilla call option was implemented in Python with a 50,000 sample size and resulted in an estimated price of \$8.740.

In comparison, the price calculated with the CEV model and non-central chi-squared distribution is \$8.702.

Although this is a relatively small difference on 4c on the unit total price, it could account for a significant cost difference when scaled to a large number of units.

\section{Part 4: Results}

The results are clearly conveyed in plots comparing the Monte Carlo estimates with closed-form solutions.In each of the following plots, the margin of error has been plotted in red, using a margin of three standard deviations.

\begin{center}
\adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_33_0.png}
\end{center}

\begin{center}
\adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_35_0.png}
\end{center}

It is evident that there is a discrepancy. Upon further investigation, for the Heston model, \[v_0 = 0.06\] but \[v_0 = (stock volatility)^{0.5}\] so \[stock volatility = .06^{0.5}= 0.2449\]
Note that $\sigma$ under Heston model refers to volatility of stock volatility.

Under our stock price Monte Carlo calculation, the default stock volatility is 0.0948 (given by  0.3*(100)*-.25 ). Thus its much less than Heston. To have the same initial stock volatility, we find a new value for $\sigma$ by equating \[\sigma(S_{ti})^{\gamma-1} = \sqrt{0.06}\] giving us \[\sigma = 0.775\]

We then find that our newly calculated Monte Carlo calculated call prices are aligned with the Fourier prices.

\begin{center}
\adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_39_0.png}
\end{center}

\nocite{*}
\printbibliography[title=References]

\end{document}

### 2020-04-26 week5/Report.tex
Added Part 1 to the Report

--- 2020-04-12 Submission1.tex
@@
 
-\title{Price a European Up-and-out Call Option}
+\title{Price a Vanilla European Call Option}
 
@@
 
-\date{April. 8, 2020} % if this is omitted, the current date is used for the title page
+\date{April. 26, 2020} % if this is omitted, the current date is used for the title page
 \maketitle
@@
 \noindent
-\textbf{Keywords:} Exotic Options, European up-and-out call option,  Black-Scholes-Merton model and Geometric Brownian Motion.
+\textbf{Keywords:} European Options, Heston model,  Constant Elasticity of Variance (CEV) model and Stochastic Volatility.
 
@@
 \begin{abstract}
-This report presents the results of the simulation of a European up-and-out call option over twelve months.
-The Black-Scholes-Merton model will be used to implement Monte Carlo estimations using Python code.
-The estimations will simulate paths for the underlying share and the counterparty's firm value using varying sample sizes, and determine estimates of both the default-free value of the option and the Credit Valuation Adjustment (CVA).
-Following from these it is simple to price the option incorporating counterparty risk, given by the default-free price less the CVA.
+    In this paper, we price a vanilla European call option under the Heston model and then simulate the monthly share price over a year using the Constant Elasticity of Variance (CEV) model, with the assumption of constant volatility each month.
+Monte Carlo simulations with varying sample sizes are run and the results are plotted against the closed form value for comparison.
 \end{abstract}
@@
 }
-A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.
-The payoff of an up-and-out option at maturity $T$ is given by,
+We initialize most variables as given by the question.
 
-\[
-Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
-\]
-Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.
-This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level.
-\\
+\begin{itemize}
+    \item Option maturity is one year
+    \item The option is struck at-the-money
+    \item The current share price is \$100
+    \item The risk-free continuously compounded interest rate is 8%
+    \item The volatility for the underlying share is 30%
+\end{itemize}
 
-The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.
-This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}.
-Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.
+\section{Fourier pricing technique under Heston model dynamics
+}
 
-Possible paths for the up-and-out barrier option payoff would look similar to the chart below, where two of the paths have crossed the barrier and resulted in zero payoff, but the other three have not crossed the barrier and behave like a vanilla option.
+Black-Scholes option pricing models assumed volatility of the underlying assets to be constant or a predetermined function of time, we will now implement a model which features instantaneous variance of asset price using volatility that evolves stochastically in time.
+Although there are several models incorporating stochastic volatility including introduced by Hull and White \cite{HW1}, Stein and Stein \cite{SS1} and Heston \cite{Heston1} \cite{Heston2}, we will implement Heston's constant interest rate model.
 
-\begin{figure}
-    \centering
-    \caption{Simulated Payoffs for an Up-and-out Barrier Option}
-    \includegraphics{images/barrier-example.png}
-\end{figure}
+With the assumption that the underlying share follows the Heston model dynamics, the additional parameters required are specified as follows:
+\begin{itemize}
+    \item $\nu_0 = 0.06$
+    \item $\kappa = 9$
+    \item $\theta = 0.06$
+    \item $\rho = -0.4$
+\end{itemize}
 
-We initialize most variables as given by the question. We assume the
-counterparty firm's value is at 200, as this is above the counterparty's
-debt due in one year. Also, we calculate the default-free value of our
-option to be 6.60, so we select a firm value not too distant such that
-the CVA value we calculate is not negligible. For example, if we chose
-counterparty firm value as 1,000, the CVA would be 0.000.
+    The Characteristic function is implemented using a function presented by
+Albrecher et al \cite{AMST1}. The function is written as:
+\[\phi_{S_T} = exp(C(\tau;u)+D(\tau;u)v_t + iu \log(S_t) )\]
+
+Where,
+
+\[C(\tau;u) = ri\tau u + \theta \kappa [\tau x\_ - \frac{1}{a}\log(\frac{1-ge^{d\tau}}{1-g})],\]
+
+\[D(\tau;u) = (\frac{1-e^{d\tau}}{1-ge^{d\tau}})x\_,\]
+
+\[\tau = T -t ,\]
+
+\[ g = \frac{x\_}{x_+},\]
+
+\[ x_\pm = \frac{b\pm d}{2a},\]
+
+\[ d = \sqrt{b^2 - 4ac},\]
+
+\[ c = - \frac{u^2 + ui}{2},\]
+
+\[ b = \kappa - \rho \sigma iu,\]
+
+\[ a = \frac {\sigma^2}{2}\]
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{2}{\boxspacing}
+\prompt{In}{incolor}{}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{} Initialize problem parameters}
-\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1} \PY{c+c1}{\PYZsh{} option maturity}
-\PY{n}{L} \PY{o}{=} \PY{l+m+mi}{150} \PY{c+c1}{\PYZsh{} up\PYZhy{}and\PYZhy{}out barrier}
-\PY{n}{S0} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} current share price}
-\PY{n}{K} \PY{o}{=} \PY{l+m+mi}{100} \PY{c+c1}{\PYZsh{} strike price, at\PYZhy{}the\PYZhy{}money}
-\PY{n}{risk\PYZus{}free} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{08} \PY{c+c1}{\PYZsh{} risk\PYZhy{}free rate}
-\PY{n}{sigma} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{3} \PY{c+c1}{\PYZsh{} volatility}
-\PY{n}{v\PYZus{}0} \PY{o}{=} \PY{l+m+mi}{200} \PY{c+c1}{\PYZsh{} counterparty firm current value (Our assumption) }
-\PY{n}{sigma\PYZus{}firm} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{25} \PY{c+c1}{\PYZsh{} volatility for the counterparty\PYZsq{}s firm}
-\PY{n}{debt} \PY{o}{=} \PY{l+m+mi}{175} \PY{c+c1}{\PYZsh{} counterparty\PYZsq{}s debt, due in one year }
-\PY{n}{corr} \PY{o}{=} \PY{o}{.}\PY{l+m+mi}{2} \PY{c+c1}{\PYZsh{} correlation}
-\PY{n}{recovery\PYZus{}rate} \PY{o}{=} \PY{l+m+mf}{0.25} \PY{c+c1}{\PYZsh{} recovery rate}
-\PY{c+c1}{\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}\PYZsh{}}
-\PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
-\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
+\PY{c+c1}{\PYZsh{}Characteristic function code}
+
+\PY{n}{a} \PY{o}{=} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}
+
+\PY{k}{def} \PY{n+nf}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{kappa} \PY{o}{\PYZhy{}} \PY{n}{rho}\PY{o}{*}\PY{n}{sigma}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}
+
+\PY{k}{def} \PY{n+nf}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{u}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{+}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}
+
+\PY{k}{def} \PY{n+nf}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{\PYZhy{}}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{a}\PY{o}{*}\PY{n}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{+}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{n}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{n}{val1} \PY{o}{=} \PY{n}{T}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{a}
+    \PY{k}{return} \PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u} \PY{o}{+} \PY{n}{theta}\PY{o}{*}\PY{n}{kappa}\PY{o}{*}\PY{n}{val1}
+
+\PY{k}{def} \PY{n+nf}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{n}{val1} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
+    \PY{n}{val2} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
+    \PY{k}{return} \PY{p}{(}\PY{n}{val1}\PY{o}{/}\PY{n}{val2}\PY{p}{)}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)} \PY{o}{+} \PY{n}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{v0} \PY{o}{+} \PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{adj\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}\PY{o}{/}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}
 \end{Verbatim}
@@
 
-\section{Simulated Paths for the Underlying Share and Counterparty Firm
-}
-
- In order to simulate paths for the underlying share and the firm,  we use a Cholesky decomposition to generate the correlated price paths.
+    Now we vectorize the code, calculate an estimate for integrals and
+calculate the Fourier estimate of our call price.
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{3}{\boxspacing}
+\prompt{In}{incolor}{}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
+\PY{n}{delta\PYZus{}t} \PY{o}{=} \PY{n}{t\PYZus{}max}\PY{o}{/}\PY{n}{N}
+\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,}\PY{n}{N}\PY{p}{,}\PY{n}{N}\PY{p}{)}
+\PY{n}{t\PYZus{}n} \PY{o}{=} \PY{p}{(}\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}
 
-\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
-    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
-    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}
+\PY{c+c1}{\PYZsh{}Integral calculations}
+\PY{n}{first\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{adj\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
+\PY{n}{second\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
 
-    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
-    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
-    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
-    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
-
-    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
-\end{Verbatim}
-\end{tcolorbox}
-
-    To double check that the stock prices and firm values monthly returns
-are correlated, we check them as follows, generating 20 different price
-paths with 10,000 timesteps.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{4}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
-\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
-\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{10000}\PY{p}{)}
-
-\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
-
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
-    \PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}
-    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Pearson correlation coefficient : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{, Two\PYZhy{}tailed p\PYZhy{}value }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{pearson}\PY{p}{,} \PY{n}{p\PYZus{}value}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.198, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.184, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.203, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.204, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.209, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.198, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.215, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.187, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.208, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.196, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.192, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.186, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.204, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.205, Two-tailed p-value 0.000
-Pearson correlation coefficient : 0.188, Two-tailed p-value 0.000
-    \end{Verbatim}
-
-    Let's try to simulate the share price with a small number of sample
-paths and visualize them over the course of 12 months
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{5}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{5}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}
-\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
-\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Share price over 12 months}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_10_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-    We can do the same thing to simulate counterparty firm's value
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{6}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{firm\PYZus{}value\PYZus{}12\PYZus{}months} \PY{o}{=} \PY{n}{share\PYZus{}and\PYZus{}firm\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
-\PY{n}{firm\PYZus{}value\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Counterparty firm}\PY{l+s+s2}{\PYZsq{}}\PY{l+s+s2}{s value over 12 months}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_12_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-     Let's visualize when the stopped process is appied
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{8}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{def} \PY{n+nf}{stop}\PY{p}{(}\PY{n}{s}\PY{p}{,} \PY{n}{cond}\PY{p}{)}\PY{p}{:}
-    \PY{n}{ret} \PY{o}{=} \PY{n}{s}\PY{o}{.}\PY{n}{copy}\PY{p}{(}\PY{p}{)}
-    \PY{n}{r} \PY{o}{=} \PY{n}{ret}\PY{p}{[}\PY{n}{cond}\PY{p}{]}
-    \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{r}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{:}
-        \PY{n+nb}{print}\PY{p}{(}\PY{n}{r}\PY{p}{)}
-        \PY{n}{ret}\PY{p}{[}\PY{n}{r}\PY{o}{.}\PY{n}{idxmin}\PY{p}{(}\PY{p}{)}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{l+m+mi}{0}
-    \PY{k}{return} \PY{n}{ret}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{9}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{o}{.}\PY{n}{apply}\PY{p}{(}\PY{k}{lambda} \PY{n}{s}\PY{p}{:} \PY{n}{stop}\PY{p}{(}\PY{n}{s}\PY{p}{,} \PY{n}{s}\PY{o}{\PYZgt{}}\PY{n}{L}\PY{p}{)}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_17_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-    We then define a function to calculate the payoff for the up-and-out call option.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{10}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
-\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
-    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
-    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
-
-\PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+\PY{c+c1}{\PYZsh{}Call value}
+\PY{n}{fourier\PYZus{}call\PYZus{}val} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{first\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{second\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}
+\PY{n}{fourier\PYZus{}call\PYZus{}val}
 \end{Verbatim}
@@
             \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
-\prompt{Out}{outcolor}{10}{\boxspacing}
+\prompt{Out}{outcolor}{}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-array([ 0.        , 37.34484527, 43.05073004,  0.        ,  7.00008561])
-\end{Verbatim}
-\end{tcolorbox}
-We now create the share and firm price paths for sample sizes 1000, 2000, \ldots{}., 50000, as required for part 1 of the assignment.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{11}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
-\PY{n}{firm\PYZus{}val\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
-
-\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
-
-\PY{k}{for} \PY{n}{sample\PYZus{}size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
-    \PY{n}{share\PYZus{}val}\PY{p}{,} \PY{n}{firm\PYZus{}val} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}
-
-    \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{share\PYZus{}val}
-    \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{firm\PYZus{}val}
+13.734895692109077
 \end{Verbatim}
@@
 
-    We now plot the share and firm price paths for sample size of 1000.
+    To see the effectiveness of the pricing option under Heston dynamics we
+will also price the call option under Black-Scholes assumption.
 
     \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{12}{\boxspacing}
+\prompt{In}{incolor}{}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
-\end{Verbatim}
-\end{tcolorbox}
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_23_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{13}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price value for sample size of 1000}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\PY{c+c1}{\PYZsh{} Code for analytical solution for vanilla European Call option}
+\PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{o}{/}\PY{n}{K}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{r} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}
+\PY{n}{d\PYZus{}2\PYZus{}stock} \PY{o}{=} \PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}
+
+\PY{n}{analytic\PYZus{}callprice} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}1\PYZus{}stock}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}2\PYZus{}stock}\PY{p}{)}
+\PY{n}{analytic\PYZus{}callprice}
 \end{Verbatim}
@@
 
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_24_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-\section{Monte Carlo Estimations
-}
-
-\subsection{Default-Free Value Estimation}
-To calculate Monte Carlo estimate of the default-free option value, we
-calculate the average payoff of the 1000s of sample price paths, to
-estimate the price of the option
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{14}{\boxspacing}
+            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
+\prompt{Out}{outcolor}{}{\boxspacing}
 \begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{} Estimate the default\PYZhy{}free value of the option:}
-\PY{n}{option\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-\PY{n}{option\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-
-\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
-    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
-    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
-    \PY{n}{option\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
-    \PY{n}{option\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
+15.711312547892973
 \end{Verbatim}
@@
 
-    Prices of default-free option at various sample sizes:
+\section{Simulate a share price path using CEV Model
+}
 
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{15}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{option\PYZus{}estimate}\PY{p}{)}\PY{p}{)}\PY{p}{:}
-    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, Option value: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{option\PYZus{}estimate}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-sample size: 1000, Option value: 6.853
-sample size: 2000, Option value: 6.826
-sample size: 3000, Option value: 6.831
-sample size: 4000, Option value: 6.739
-sample size: 5000, Option value: 6.551
-sample size: 6000, Option value: 6.871
-sample size: 7000, Option value: 6.713
-sample size: 8000, Option value: 7.028
-sample size: 9000, Option value: 6.412
-sample size: 10000, Option value: 6.810
-sample size: 11000, Option value: 6.831
-sample size: 12000, Option value: 6.704
-sample size: 13000, Option value: 6.682
-sample size: 14000, Option value: 6.760
-sample size: 15000, Option value: 6.619
-sample size: 16000, Option value: 6.693
-sample size: 17000, Option value: 6.694
-sample size: 18000, Option value: 6.678
-sample size: 19000, Option value: 6.580
-sample size: 20000, Option value: 6.678
-sample size: 21000, Option value: 6.726
-sample size: 22000, Option value: 6.587
-sample size: 23000, Option value: 6.754
-sample size: 24000, Option value: 6.784
-sample size: 25000, Option value: 6.670
-sample size: 26000, Option value: 6.656
-sample size: 27000, Option value: 6.713
-sample size: 28000, Option value: 6.706
-sample size: 29000, Option value: 6.748
-sample size: 30000, Option value: 6.612
-sample size: 31000, Option value: 6.620
-sample size: 32000, Option value: 6.870
-sample size: 33000, Option value: 6.738
-sample size: 34000, Option value: 6.744
-sample size: 35000, Option value: 6.683
-sample size: 36000, Option value: 6.700
-sample size: 37000, Option value: 6.672
-sample size: 38000, Option value: 6.694
-sample size: 39000, Option value: 6.678
-sample size: 40000, Option value: 6.676
-sample size: 41000, Option value: 6.781
-sample size: 42000, Option value: 6.623
-sample size: 43000, Option value: 6.614
-sample size: 44000, Option value: 6.674
-sample size: 45000, Option value: 6.676
-sample size: 46000, Option value: 6.740
-sample size: 47000, Option value: 6.732
-sample size: 48000, Option value: 6.706
-sample size: 49000, Option value: 6.649
-sample size: 50000, Option value: 6.628
-    \end{Verbatim}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{16}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_30_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-\subsection{Credit Valuation Adjustment Estimation}
-
-To calculate Monte Carlo estimate of the credit value adjustment, we
-calculate the average loss of the 1000s of sample price paths, which
-happens when we both see a gain in the option with hold and when the
-counterparty firm value is less than its debt.
-
-As per notes, we assume that default can only occur at time T, and firm
-defaults if the firm value is below firm debt amount
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{17}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{def} \PY{n+nf}{terminal\PYZus{}value}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{T}\PY{p}{)}\PY{p}{:} \PY{c+c1}{\PYZsh{}applies to both firm and stock}
-    \PY{k}{return} \PY{n}{S\PYZus{}0} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)} \PY{o}{*} \PY{n}{T} \PY{o}{+} \PY{n}{sigma} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)} \PY{o}{*} \PY{n}{Z}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{18}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{cva\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-\PY{n}{cva\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-
-\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
-    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
-    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
-    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
-    \PY{n}{cva\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
-    \PY{n}{cva\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
-
-\end{Verbatim}
-\end{tcolorbox}
-
-    Credit value adjustment at various sample sizes:
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{19}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{cva\PYZus{}estimate}\PY{p}{)}\PY{p}{)}\PY{p}{:}
-    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, CVA: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{cva\PYZus{}estimate}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Sample size: 1000, CVA: 0.856
-Sample size: 2000, CVA: 0.906
-Sample size: 3000, CVA: 0.974
-Sample size: 4000, CVA: 0.977
-Sample size: 5000, CVA: 0.908
-Sample size: 6000, CVA: 0.957
-Sample size: 7000, CVA: 0.953
-Sample size: 8000, CVA: 1.035
-Sample size: 9000, CVA: 0.923
-Sample size: 10000, CVA: 0.977
-Sample size: 11000, CVA: 0.937
-Sample size: 12000, CVA: 0.977
-Sample size: 13000, CVA: 0.968
-Sample size: 14000, CVA: 0.947
-Sample size: 15000, CVA: 1.021
-Sample size: 16000, CVA: 0.948
-Sample size: 17000, CVA: 0.906
-Sample size: 18000, CVA: 0.918
-Sample size: 19000, CVA: 0.960
-Sample size: 20000, CVA: 0.958
-Sample size: 21000, CVA: 0.937
-Sample size: 22000, CVA: 0.928
-Sample size: 23000, CVA: 0.951
-Sample size: 24000, CVA: 1.024
-Sample size: 25000, CVA: 0.931
-Sample size: 26000, CVA: 0.905
-Sample size: 27000, CVA: 0.913
-Sample size: 28000, CVA: 0.966
-Sample size: 29000, CVA: 0.933
-Sample size: 30000, CVA: 0.917
-Sample size: 31000, CVA: 0.941
-Sample size: 32000, CVA: 1.025
-Sample size: 33000, CVA: 0.929
-Sample size: 34000, CVA: 0.982
-Sample size: 35000, CVA: 0.973
-Sample size: 36000, CVA: 0.944
-Sample size: 37000, CVA: 0.980
-Sample size: 38000, CVA: 0.934
-Sample size: 39000, CVA: 0.928
-Sample size: 40000, CVA: 0.950
-Sample size: 41000, CVA: 0.928
-Sample size: 42000, CVA: 0.916
-Sample size: 43000, CVA: 0.941
-Sample size: 44000, CVA: 0.951
-Sample size: 45000, CVA: 0.944
-Sample size: 46000, CVA: 0.947
-Sample size: 47000, CVA: 0.943
-Sample size: 48000, CVA: 0.954
-Sample size: 49000, CVA: 0.959
-Sample size: 50000, CVA: 0.931
-    \end{Verbatim}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{20}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{cva\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{cva\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{cva\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_36_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
-
-\section{Incorporating Counterparty Risk}
-
-We calculate the Monte Carlo estimates for the price of the option incorporating counterparty risk, given by the default-free price less the CVA.
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{21}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-
-\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
-    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
-    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
-
-    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
-    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
-
-    \PY{n}{option\PYZus{}cva\PYZus{}price} \PY{o}{=} \PY{n}{option\PYZus{}price} \PY{o}{\PYZhy{}} \PY{n}{amount\PYZus{}lost}
-
-    \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
-    \PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    Credit value adjustment at various sample sizes:
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{22}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{)}\PY{p}{)}\PY{p}{:}
-    \PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size: }\PY{l+s+si}{\PYZob{}\PYZcb{}}\PY{l+s+s2}{, CVA\PYZhy{}adjusted option value: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{p}{(}\PY{n}{i}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{o}{*}\PY{l+m+mi}{1000}\PY{p}{,}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-Sample size: 1000, CVA-adjusted option value: 5.997
-Sample size: 2000, CVA-adjusted option value: 5.920
-Sample size: 3000, CVA-adjusted option value: 5.857
-Sample size: 4000, CVA-adjusted option value: 5.763
-Sample size: 5000, CVA-adjusted option value: 5.643
-Sample size: 6000, CVA-adjusted option value: 5.913
-Sample size: 7000, CVA-adjusted option value: 5.760
-Sample size: 8000, CVA-adjusted option value: 5.993
-Sample size: 9000, CVA-adjusted option value: 5.490
-Sample size: 10000, CVA-adjusted option value: 5.834
-Sample size: 11000, CVA-adjusted option value: 5.894
-Sample size: 12000, CVA-adjusted option value: 5.726
-Sample size: 13000, CVA-adjusted option value: 5.715
-Sample size: 14000, CVA-adjusted option value: 5.814
-Sample size: 15000, CVA-adjusted option value: 5.597
-Sample size: 16000, CVA-adjusted option value: 5.745
-Sample size: 17000, CVA-adjusted option value: 5.788
-Sample size: 18000, CVA-adjusted option value: 5.760
-Sample size: 19000, CVA-adjusted option value: 5.620
-Sample size: 20000, CVA-adjusted option value: 5.720
-Sample size: 21000, CVA-adjusted option value: 5.788
-Sample size: 22000, CVA-adjusted option value: 5.659
-Sample size: 23000, CVA-adjusted option value: 5.803
-Sample size: 24000, CVA-adjusted option value: 5.760
-Sample size: 25000, CVA-adjusted option value: 5.739
-Sample size: 26000, CVA-adjusted option value: 5.751
-Sample size: 27000, CVA-adjusted option value: 5.799
-Sample size: 28000, CVA-adjusted option value: 5.740
-Sample size: 29000, CVA-adjusted option value: 5.815
-Sample size: 30000, CVA-adjusted option value: 5.695
-Sample size: 31000, CVA-adjusted option value: 5.678
-Sample size: 32000, CVA-adjusted option value: 5.845
-Sample size: 33000, CVA-adjusted option value: 5.809
-Sample size: 34000, CVA-adjusted option value: 5.762
-Sample size: 35000, CVA-adjusted option value: 5.709
-Sample size: 36000, CVA-adjusted option value: 5.756
-Sample size: 37000, CVA-adjusted option value: 5.693
-Sample size: 38000, CVA-adjusted option value: 5.760
-Sample size: 39000, CVA-adjusted option value: 5.750
-Sample size: 40000, CVA-adjusted option value: 5.726
-Sample size: 41000, CVA-adjusted option value: 5.853
-Sample size: 42000, CVA-adjusted option value: 5.707
-Sample size: 43000, CVA-adjusted option value: 5.673
-Sample size: 44000, CVA-adjusted option value: 5.724
-Sample size: 45000, CVA-adjusted option value: 5.732
-Sample size: 46000, CVA-adjusted option value: 5.793
-Sample size: 47000, CVA-adjusted option value: 5.789
-Sample size: 48000, CVA-adjusted option value: 5.753
-Sample size: 49000, CVA-adjusted option value: 5.689
-Sample size: 50000, CVA-adjusted option value: 5.697
-    \end{Verbatim}
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{23}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{+} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3} \PY{o}{*} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA\PYZhy{}adjusted option prices estimates}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Sample size (1000)}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Option value}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
+\section{Monte Carlo estimates}
 
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{Merton1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
-\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
-\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
-\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
-\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
+\bibitem{HW1} Hull, J. and White, A. (1987). The pricing of options on assets
+with stochastic volatilities. The journal of finance, 42(2):281--300.
+\bibitem{SS1} Stein, E. M. and Stein, J. C. (1991). Stock price distributions
+with stochastic volatility: an analytic approach. Review of financial
+Studies, 4(4):727--752.
+\bibitem{Heston1} Heston, S. L. (1993). A closed-form solution for options with
+stochastic volatility with applications to bond and currency options.
+Review of financial studies, 6(2):327--343.
+\bibitem{Heston2} Heston, S. L. (1997). A simple new formula for options with
+stochastic volatility.
+\bibitem{AMST1} Albrecher, H., Mayer, P., Schoutens, W. and Tistaert, J. (2007).
+``The Little Heston Trap'', Wilmott (1): 83--92.
 
 \end{thebibliography}
-\bibliographystyle{plain}
-\bibliography{template}
 

### 2020-04-26 week5/Report.tex
Report Body Finished

@@
 }
+
+In this paper we go beyond the constant volatility assumption in the Black-Scholes model.  Most of code implemented in this submission id derived from Moldule 5 \cite{M5} of the course.
+
 We initialize most variables as given by the question.
@@
     \item The current share price is \$100
-    \item The risk-free continuously compounded interest rate is 8%
-    \item The volatility for the underlying share is 30%
+    \item The risk-free continuously compounded interest rate is 8\%
+    \item The volatility for the underlying share is 30\%
 \end{itemize}
@@
 }
+Cox \cite{Cox1} developed the constant elasticity of variance (CEV) option pricing model, it attempts to capture stochastic volatility and is given by:
+
+\[dS_t =  \mu S_t dt + \sigma  S^\gamma _t dW_t\]
+
+If $\gamma = 1$ this model return the same value as Black-Scholes model, however if the value of $\gamma < 1 $ we experience an effect called leverage effect where the volatility increases as the price decreases over subsequent time periods.
+
+Based on the assumption that $\sigma(t_i,t_{i+1}) = \sigma(S_{ti})^{\gamma-1}$, where $\sigma = 0.3$ and $\gamma = 0.75$.
+We can simulate the next step in a share price path using the following formula:
+$$S_{t_{i+1}} = S_{t_i}e^{(r - \frac{\sigma^2 (t_i,t_{i+1})}{2})(t_{i+1}-t_i)+\sigma(t_i, t_{i+1})\sqrt{t_{i+1}-t_i}Z}$$
+where $S_{ti}$ is the share price at time $t_i$, $\sigma(t_i, t_{i+1})$ is the volatility for the period $[t_i,t_{i+1}]$, r is the risk-free interest rate, and Z~N(0, 1)
+
+First, we define our helper functions. The next\_share\_price function
+is used to calculate the evolution of the share price at t+1, from the
+share price at t. We generate the random variable Z from within this
+function. The effective sigma is also written as a function of the share
+price at t.
+
+Just for exploration purposes, we also added a varying\_vol flag, to
+allow us to switch between a constant volatility and varying volatility.
+We use the initial stock price instead of the previous price when
+assuming a contant volatility.
+
+The other function is the generate\_share\_price\_path function. We
+first create an empty numpy array of shape (sample\_size x timesteps+1).
+Note the addition of one element to the timestep, as the first element
+is equal to the initial stock price. We then iterate through each path,
+and each timestep, applying the next\_share\_price function against the
+previous share price. We then convert the result into a pandas DataFrame
+and return the results.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{7}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{dT}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
+    \PY{n}{Z} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size}\PY{o}{=}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+    \PY{k}{if} \PY{n}{varying\PYZus{}vol}\PY{p}{:}
+        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+    \PY{k}{else}\PY{p}{:}
+        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+
+    \PY{k}{return} \PY{n}{prev\PYZus{}price}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{r}\PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{sigma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
+    \PY{n}{df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{p}{[}\PY{n}{S0}\PY{p}{]}\PY{o}{*}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+    \PY{k}{for} \PY{n}{t} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{timesteps}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{:}
+        \PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{p}{]} \PY{o}{=} \PY{n}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{p}{)}
+    \PY{k}{return} \PY{n}{df}\PY{o}{.}\PY{n}{T}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{8}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{patches} \PY{k}{as} \PY{n+nn}{mpatches}
+\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{10}
+\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
+
+\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{)}
+\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{l+m+mf}{1.0}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
+
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Timestep}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{red\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CEV}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{blue\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{BSM}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{handles}\PY{o}{=}\PY{p}{[}\PY{n}{red\PYZus{}patch}\PY{p}{,} \PY{n}{blue\PYZus{}patch}\PY{p}{]}\PY{p}{,} \PY{n}{loc}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{upper left}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CEV vs BSM Stock Price Paths}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    Next, we create a python dictionary called share\_price\_paths, to hold
+our results for part 2. The key of this dictionary would be the number
+of sample price paths, while the values would be the dataframes
+containing the price paths. We also track the rough processing time
+required at each step, by printing the time when each iteration
+completes.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{9}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k+kn}{import} \PY{n+nn}{time}
+
+\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
+\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
+
+\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Start generating share price path}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{start} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
+\PY{k}{for} \PY{n}{sample\PYZus{}size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
+    \PY{n}{share\PYZus{}val} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
+
+    \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{share\PYZus{}val}
+    \PY{c+c1}{\PYZsh{}print(\PYZdq{}Updated for sample size \PYZob{}\PYZcb{} at \PYZob{}\PYZcb{}\PYZdq{}.format(sample\PYZus{}size, datetime.datetime.now().strftime(\PYZsq{}\PYZpc{}H:\PYZpc{}M\PYZsq{})))}
+\PY{n}{end} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Generating all samples paths takes }\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{(end \PYZhy{} start):.2f\PYZcb{}s}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Start generating share price path
+Generating all samples paths takes 2.58s
+    \end{Verbatim}
+
+    To display our output, we show the first 10 price paths generated by our
+iteration with 1000 samples:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{10}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}
+\end{Verbatim}
+\end{tcolorbox}
+
+            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
+\prompt{Out}{outcolor}{10}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+             0           1           2           3           4           5  \textbackslash{}
+0   100.000000  100.000000  100.000000  100.000000  100.000000  100.000000
+1    99.626771   99.374526  100.689569   97.065445  106.862386   99.918343
+2   103.745565   96.967926  102.622183   96.451414  106.332275   96.640428
+3   107.154631   96.585243  105.974778   93.207852  100.177288   99.129417
+4   111.716818   95.838855  101.540594   94.146336   98.646601  102.592136
+5   120.620494   93.477848  100.930914   94.502805  100.662067  103.175996
+6   122.217586   87.674152  101.799340   91.076602  101.876289  102.336328
+7   123.138256   87.108925  103.904210   94.061221  106.060742  103.426255
+8   129.359695   87.871374  100.925245   92.948402  115.010833   98.206543
+9   123.575048   87.571414  105.883449   95.799071  117.769685   97.640631
+10  125.486476   88.836040  104.337774   96.829970  119.866089  100.623917
+11  124.538067   92.114326  106.173600   98.493852  118.497793   99.093147
+12  123.548415   92.619346  104.478810   98.081928  114.719969   94.669329
+
+             6           7           8           9
+0   100.000000  100.000000  100.000000  100.000000
+1   106.483031  100.796117  100.030802  102.593647
+2   105.512423  101.627748   98.448810  103.179244
+3   107.821291   98.518154   97.598741  103.563761
+4   108.394844   97.918995   99.489053  110.865271
+5   108.425203   99.326116   97.269739  108.916593
+6   107.844372  103.199284   98.432527  108.089622
+7   108.269775  100.286497  101.084604  107.860547
+8   108.268731   99.113198  101.552266  103.792957
+9   103.400905   98.076554  100.633537  106.623775
+10  107.548810   98.062335   97.583078  110.004438
+11  104.394412   98.481303   94.325492  107.980799
+12  103.306627   95.171645   94.012006  108.960908
+\end{Verbatim}
+\end{tcolorbox}
+
+    Next, we plot the price paths for the iteration with 1000 samples,
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{11}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Timestep}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Share price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Sample of 1000 Share Price Paths}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_23_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 
 \section{Monte Carlo estimates}
+
+    Using Monte Carlo, we calculate the price of the vanilla call option as
+follows:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{12}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{price\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{price\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{k}{for} \PY{n}{size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
+    \PY{n}{S\PYZus{}Ts} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{l+m+mi}{12}\PY{p}{,} \PY{p}{:}\PY{p}{]}
+    \PY{n}{payoff} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{S\PYZus{}Ts} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
+    \PY{n}{discounted\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoff}
+    \PY{n}{price\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n}{price\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{size}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{13}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{The price estimated by Monte Carlo when using sample size of 50,000 is : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+The price estimated by Monte Carlo when using sample size of 50,000 is : 8.694
+    \end{Verbatim}
+
+We then compare with calculation of CEV model using noncentralchi-squared
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{14}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
+\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{pyplot} \PY{k}{as} \PY{n+nn}{plt}
+\PY{k+kn}{from} \PY{n+nn}{scipy}\PY{n+nn}{.}\PY{n+nn}{stats} \PY{k+kn}{import} \PY{n}{ncx2}
+
+\PY{n}{S0} \PY{o}{=} \PY{l+m+mi}{100}
+\PY{n}{sigma} \PY{o}{=} \PY{l+m+mf}{0.3}
+\PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.75}
+\PY{n}{r} \PY{o}{=} \PY{l+m+mf}{0.08}
+\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{15}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{z} \PY{o}{=} \PY{l+m+mi}{2} \PY{o}{+} \PY{l+m+mi}{1}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}
+\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{K}\PY{p}{)}\PY{p}{:}
+    \PY{n}{kappa} \PY{o}{=} \PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{n}{t}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
+    \PY{n}{x} \PY{o}{=} \PY{n}{kappa}\PY{o}{*}\PY{n}{S0}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{n}{t}\PY{p}{)}
+    \PY{n}{y} \PY{o}{=} \PY{n}{kappa}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{p}{)}
+    \PY{k}{return} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{ncx2}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{y}\PY{p}{,}\PY{n}{z}\PY{p}{,}\PY{n}{x}\PY{p}{)}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{t}\PY{p}{)}\PY{o}{*}\PY{n}{ncx2}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{x}\PY{p}{,}\PY{n}{z}\PY{o}{\PYZhy{}}\PY{l+m+mi}{2}\PY{p}{,}\PY{n}{y}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{16}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{cev\PYZus{}call\PYZus{}price} \PY{o}{=} \PY{n}{C}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{l+m+mi}{100}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{17}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{The price calculated via CEV model using noncentral chi\PYZhy{}squared distribution is : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{cev\PYZus{}call\PYZus{}price}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+The price calculated via CEV model using noncentral chi-squared distribution is
+: 8.702
+    \end{Verbatim}
+
+    We plot the prices of our Monte Carlo estimates against the CEV
+noncentral chi-squared distribution prices calculated from Part 1 above:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{18}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{n}{cev\PYZus{}call\PYZus{}price}\PY{p}{]}\PY{o}{*}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CEV Call Price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Monte Carlo Estimates}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_35_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    We also plot the prices of our Monte Carlo estimates against the Fourier
+Call prices calculated from Part 1 above:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{19}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{n}{fourier\PYZus{}call\PYZus{}val}\PY{p}{]}\PY{o}{*}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Fourier Call Price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Monte Carlo Estimates}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_37_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    We notice that there is a discrepency. Upon further investigation, for
+the Heston model, v\_0 = 0.06 (v\_0 = stock volatility \^{} 0.5), so
+stock volatility = .06**0.5= 0.2449. Note that sigma under Heston model
+refers to volatility of stock volatility
+
+Under our stock price Monte Carlo calculation, the default stock
+volatility is 0.0948 (given by 0.3\emph{(100)}-.25 ). Thus its much less
+than Heston. To have the same initial stock volatility, we find a new
+value for \(\sigma\) by equating
+\(\sigma(S_{ti})^{\gamma-1} = \sqrt{0.06}\), giving us
+\(\sigma = 0.775\).
+
+We then find that our newly calculated Monte Carlo calculated call
+prices are aligned with the Fourier prices.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{20}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{sigma\PYZus{}const} \PY{o}{=} \PY{l+m+mf}{0.775}
+
+\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
+\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}
+
+\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
+
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Start generating share price path}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{start} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
+\PY{k}{for} \PY{n}{sample\PYZus{}size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
+    \PY{n}{share\PYZus{}val} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
+
+    \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{share\PYZus{}val}
+    \PY{c+c1}{\PYZsh{}print(\PYZdq{}Updated for sample size \PYZob{}\PYZcb{} at \PYZob{}\PYZcb{}\PYZdq{}.format(sample\PYZus{}size, datetime.datetime.now().strftime(\PYZsq{}\PYZpc{}H:\PYZpc{}M\PYZsq{})))}
+\PY{n}{end} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Generating all samples paths takes }\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{(end \PYZhy{} start):.2f\PYZcb{}s}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Start generating share price path
+Generating all samples paths takes 2.10s
+    \end{Verbatim}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{21}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{price\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{price\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{k}{for} \PY{n}{size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
+    \PY{n}{S\PYZus{}Ts} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{l+m+mi}{12}\PY{p}{,} \PY{p}{:}\PY{p}{]}
+    \PY{n}{payoff} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{S\PYZus{}Ts} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
+    \PY{n}{discounted\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoff}
+    \PY{n}{price\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
+    \PY{n}{price\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{size}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{22}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{n}{fourier\PYZus{}call\PYZus{}val}\PY{p}{]}\PY{o}{*}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Fourier Call Price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Monte Carlo Estimates}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_41_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
 
@@
 ``The Little Heston Trap'', Wilmott (1): 83--92.
+\bibitem{Cox1}  Cox, John. "Notes on option pricing I: Constant elasticity of variance diffusions." Unpublished note, Stanford University, Graduate School of Business (1975).
+\bibitem{M5} MScFE630 Computational Finance Module 5: Monte Carlo Methods for Risk Management
 

### 2020-04-27 week5/Report.tex
Report Body Finished typo
Added conclusion, spelling fix, adjusted error margin plots

@@
 
-In this paper we go beyond the constant volatility assumption in the Black-Scholes model.  Most of code implemented in this submission id derived from Moldule 5 \cite{M5} of the course.
+In this paper we go beyond the constant volatility assumption in the Black-Scholes model.  Most of code implemented in this submission is derived from Module 5 \cite{M5} of the course.
 
@@
 
+A vanilla European call option was priced for a fluctuating volatility condition, using the Heston model.
+The call price was evaluated as \$13.73, which was verified to be similar to - but lower than - a constant volatility estimate using the Black-Scholes model at \$15.71.
+
+Initially the values calculated for the underlying share price did not agree as expected, with the estimates well outside the expected error range.
+This was because the volatility term was not equivalent in the two different calculation methods.
+After resolving this, the CEV model calculated a price of \$8.70 for the underlying share, which agreed closely with the Monte Carlo estimate of \$8.69.
+This represents an absolute error of 1c and a relative discrepancy of approximately 0.1%.
+
+The agreement between the results from various methods, although expected, provides confidence to choose the most suitable method for a situation with the knowledge that the results are accurate within a small margin of error.
+
 \newpage

### 2020-05-10 week7/Report.tex
Added Report + Intro

--- 2020-04-26 week5/Report.tex
@@
 
-\title{Price a Vanilla European Call Option}
+\title{Simulate Asset Price Evolutions and Reprice Risky up-and-out Call Option}
 
@@
 
-\date{April. 26, 2020} % if this is omitted, the current date is used for the title page
+\date{May. 10, 2020} % if this is omitted, the current date is used for the title page
 \maketitle
@@
 \noindent
-\textbf{Keywords:} European Options, Heston model,  Constant Elasticity of Variance (CEV) model and Stochastic Volatility.
+\textbf{Keywords:} European Options, Non-constant interest rate,  Local volatility, LIBOR forward rates, Zero-coupon bond and Stochastic Volatility.
 
@@
 \begin{abstract}
-    In this paper, we price a vanilla European call option under the Heston model and then simulate the monthly share price over a year using the Constant Elasticity of Variance (CEV) model, with the assumption of constant volatility each month.
-Monte Carlo simulations with varying sample sizes are run and the results are plotted against the closed form value for comparison.
+This report presents the results of the simulation of a European up-and-out call option over twelve months, but the difference between this submission and submission 1 is the implementation of a non-constant interest rate and local volatility.
+We use LIBOR forward rate model to simulate interest rates.
+We also use discount factor to value the option without default risk and then the value of the option with counterparty default risk.
+
 \end{abstract}
@@
 }
+
+In this paper we go beyond the constant risk-free continuously compounded rate.
+There are several models to implement stochastic interest rates.
+The short rate models which describe instantaneous continuously-compounded interest rate at time $t , r_t$ include the Vasicek model introduced in \cite{Vas1}, Mamon in \cite{Mamon1} advances this model by presenting approaches in obtaining the closed-form solution using the Vasicek model.
+Under the Vasicek model the short rate dynamics is given by,\\
+
+\[
+d r_t= \alpha (b - r_t) dt + \sigma dW_t
+\]
+
+Where $W_t$ is Brownian motion, $b$ is the level to which the short rate will tend in the long run, $\alpha$ is the rate at which the short rate will tend towards $b$ and $\sigma$ is the volatility of the short rate.
+The stochastic differential equation can be solved to give $r_t$
+
+\[
+r_t= e^{-\alpha t} [r_0 + b(e^{\alpha t} - 1)+\int^t_0 \sigma e^{\alpha s} dW_s ] 
+\]
+\\
+
+Cox, Ingersoll and Ross also presented a stochastic differential equation for short term rates in \cite{CIR1} given by
+\[
+d r_t= \alpha (b - r_t) dt + \sigma \sqrt{r_t} dW_t
+\]
+This model prevents the short from becoming 0 but offers no closed form solution\\
+
+The Hull-White model described in \cite{HW1} also presents stochastic differential equation for the short term rate,
+
+\[
+d r_t= (\theta(t) - \alpha(t) r_t) dt + \sigma (t) dW_t
+\]
+where $\theta(t) = \alpha b$ which is a non constant term, allowing the mean reversion level to vary. \\
+
+The model we implement in this assignment is the LIBOR forward rate model to simulate interest rates.
+The initial values for the LIBOR forward rates need to be calibrated to the market forward rates which can be deduced through the market zero-coupon bond prices.
+This continuously compounded interest rate is given by,
+
+\[
+e^{r_{ti} (t_{i+1} - t_i)}= 1 + L(t_i,t_{i+1})(t_{i+1} -t_i )
+\]
+
+Most of code implemented in this submission is derived from Module 6 \cite{M6} and Module 7 \cite{M7} of the course.
+
 We initialize most variables as given by the question.
@@
     \item The current share price is \$100
-    \item The risk-free continuously compounded interest rate is 8%
-    \item The volatility for the underlying share is 30%
+    \item The up-and-out barrier for the option is \$150
+    \item The risk-free continuously compounded interest rate is 8\%
+    \item The volatility for the underlying share is 30\%
+    \item The volatility for counterparty's firm value is 25\%
+    \item The counterparty's debt, due in one year, is  \$175
+    \item The current firm value for the counterparty is \$200
+    \item The correlation between the counterparty and the stock is constant at 0.2
+    \item The recovery rate with the counterparty is 25\%
+
 \end{itemize}
 
-\section{Fourier pricing technique under Heston model dynamics
+\section{LIBOR forward rates, stock paths, and counterparty firm values.
 }
 
-Black-Scholes option pricing models assumed volatility of the underlying assets to be constant or a predetermined function of time, we will now implement a model which features instantaneous variance of asset price using volatility that evolves stochastically in time.
-Although there are several models incorporating stochastic volatility including introduced by Hull and White \cite{HW1}, Stein and Stein \cite{SS1} and Heston \cite{Heston1} \cite{Heston2}, we will implement Heston's constant interest rate model.
-
-With the assumption that the underlying share follows the Heston model dynamics, the additional parameters required are specified as follows:
-\begin{itemize}
-    \item $\nu_0 = 0.06$
-    \item $\kappa = 9$
-    \item $\theta = 0.06$
-    \item $\rho = -0.4$
-\end{itemize}
-
-    The Characteristic function is implemented using a function presented by
-Albrecher et al \cite{AMST1}. The function is written as:
-\[\phi_{S_T} = exp(C(\tau;u)+D(\tau;u)v_t + iu \log(S_t) )\]
-
-Where,
-
-\[C(\tau;u) = ri\tau u + \theta \kappa [\tau x\_ - \frac{1}{a}\log(\frac{1-ge^{d\tau}}{1-g})],\]
-
-\[D(\tau;u) = (\frac{1-e^{d\tau}}{1-ge^{d\tau}})x\_,\]
-
-\[\tau = T -t ,\]
-
-\[ g = \frac{x\_}{x_+},\]
-
-\[ x_\pm = \frac{b\pm d}{2a},\]
-
-\[ d = \sqrt{b^2 - 4ac},\]
-
-\[ c = - \frac{u^2 + ui}{2},\]
-
-\[ b = \kappa - \rho \sigma iu,\]
-
-\[ a = \frac {\sigma^2}{2}\]
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{}Characteristic function code}
-
-\PY{n}{a} \PY{o}{=} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}
-
-\PY{k}{def} \PY{n+nf}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{kappa} \PY{o}{\PYZhy{}} \PY{n}{rho}\PY{o}{*}\PY{n}{sigma}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}
-
-\PY{k}{def} \PY{n+nf}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{u}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{+}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}
-
-\PY{k}{def} \PY{n+nf}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{\PYZhy{}}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{a}\PY{o}{*}\PY{n}{c}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{p}{(}\PY{n}{b}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{+}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{a}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{/}\PY{n}{xplus}\PY{p}{(}\PY{n}{u}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{n}{val1} \PY{o}{=} \PY{n}{T}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{a}
-    \PY{k}{return} \PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{o}{*}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u} \PY{o}{+} \PY{n}{theta}\PY{o}{*}\PY{n}{kappa}\PY{o}{*}\PY{n}{val1}
-
-\PY{k}{def} \PY{n+nf}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{n}{val1} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
-    \PY{n}{val2} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{g}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{T}\PY{o}{*}\PY{n}{d}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{)}
-    \PY{k}{return} \PY{p}{(}\PY{n}{val1}\PY{o}{/}\PY{n}{val2}\PY{p}{)}\PY{o}{*}\PY{n}{xminus}\PY{p}{(}\PY{n}{u}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{C}\PY{p}{(}\PY{n}{u}\PY{p}{)} \PY{o}{+} \PY{n}{D}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{o}{*}\PY{n}{v0} \PY{o}{+} \PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{u}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{p}{)}
-
-\PY{k}{def} \PY{n+nf}{adj\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{p}{)}\PY{p}{:}
-    \PY{k}{return} \PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{u}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}\PY{o}{/}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{p}{)}
-\end{Verbatim}
-\end{tcolorbox}
-
-    Now we vectorize the code, calculate an estimate for integrals and
-calculate the Fourier estimate of our call price.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{n}{delta\PYZus{}t} \PY{o}{=} \PY{n}{t\PYZus{}max}\PY{o}{/}\PY{n}{N}
-\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,}\PY{n}{N}\PY{p}{,}\PY{n}{N}\PY{p}{)}
-\PY{n}{t\PYZus{}n} \PY{o}{=} \PY{p}{(}\PY{n}{from\PYZus{}1\PYZus{}to\PYZus{}N}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}
-
-\PY{c+c1}{\PYZsh{}Integral calculations}
-\PY{n}{first\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{adj\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
-\PY{n}{second\PYZus{}integral} \PY{o}{=} \PY{n+nb}{sum}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{n}{j}\PY{o}{*}\PY{n}{t\PYZus{}n}\PY{o}{*}\PY{n}{k\PYZus{}log}\PY{p}{)}\PY{o}{*}\PY{n}{log\PYZus{}char}\PY{p}{(}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{p}{)}\PY{o}{.}\PY{n}{imag}\PY{p}{)}\PY{o}{/}\PY{n}{t\PYZus{}n}\PY{p}{)}\PY{o}{*}\PY{n}{delta\PYZus{}t}\PY{p}{)}
-
-\PY{c+c1}{\PYZsh{}Call value}
-\PY{n}{fourier\PYZus{}call\PYZus{}val} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{first\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{/}\PY{l+m+mi}{2} \PY{o}{+} \PY{n}{second\PYZus{}integral}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{pi}\PY{p}{)}
-\PY{n}{fourier\PYZus{}call\PYZus{}val}
-\end{Verbatim}
-\end{tcolorbox}
-
-            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
-\prompt{Out}{outcolor}{}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-13.734895692109077
-\end{Verbatim}
-\end{tcolorbox}
-
-    To see the effectiveness of the pricing option under Heston dynamics we
-will also price the call option under Black-Scholes assumption.
-
-    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
-\prompt{In}{incolor}{}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-\PY{c+c1}{\PYZsh{} Code for analytical solution for vanilla European Call option}
-\PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{S0}\PY{o}{/}\PY{n}{K}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{r} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}
-\PY{n}{d\PYZus{}2\PYZus{}stock} \PY{o}{=} \PY{n}{d\PYZus{}1\PYZus{}stock} \PY{o}{\PYZhy{}} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{T}\PY{p}{)}
-
-\PY{n}{analytic\PYZus{}callprice} \PY{o}{=} \PY{n}{S0}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}1\PYZus{}stock}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{n}{T}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{norm}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{d\PYZus{}2\PYZus{}stock}\PY{p}{)}
-\PY{n}{analytic\PYZus{}callprice}
-\end{Verbatim}
-\end{tcolorbox}
-
-            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
-\prompt{Out}{outcolor}{}{\boxspacing}
-\begin{Verbatim}[commandchars=\\\{\}]
-15.711312547892973
-\end{Verbatim}
-\end{tcolorbox}
-
-\section{Simulate a share price path using CEV Model
+\section{Discount factor and Value of the Option
 }
-
-\section{Monte Carlo estimates}
 
@@
 \begin{thebibliography}{MMMMM} 
-\bibitem{HW1} Hull, J. and White, A. (1987). The pricing of options on assets
-with stochastic volatilities. The journal of finance, 42(2):281--300.
-\bibitem{SS1} Stein, E. M. and Stein, J. C. (1991). Stock price distributions
-with stochastic volatility: an analytic approach. Review of financial
-Studies, 4(4):727--752.
-\bibitem{Heston1} Heston, S. L. (1993). A closed-form solution for options with
-stochastic volatility with applications to bond and currency options.
-Review of financial studies, 6(2):327--343.
-\bibitem{Heston2} Heston, S. L. (1997). A simple new formula for options with
-stochastic volatility.
+\bibitem{Vas1} Vasicek, O. (1977). An equilibrium characterization of the term structure, Journal of financial economics 5(2): 177-188.
+\bibitem{Mamon1} Mamon, R. S. (2004). Three ways to solve for bond prices in the vasicek model, Advances in Decision Sciences 8(1): 1-14.
+\bibitem{HW1} Hull, J. and White, A. (2001). The general hull-white model and supercalibration, Financial Analysts Journal pp. 34-43.
+\bibitem{CIR1} Cox, J. C., Ingersoll Jr, J. E. and Ross, S. A. (1985). An intertemporal general equilibrium model of asset prices, Econometrica: Journal of the Econometric Society pp. 363-384.
 \bibitem{AMST1} Albrecher, H., Mayer, P., Schoutens, W. and Tistaert, J. (2007).
 ``The Little Heston Trap'', Wilmott (1): 83--92.
+\bibitem{Cox1}  Cox, John. "Notes on option pricing I: Constant elasticity of variance diffusions." Unpublished note, Stanford University, Graduate School of Business (1975).
+\bibitem{M5} MScFE630 Computational Finance Module 5: Monte Carlo Methods for Risk Management
+\bibitem{M6} MScFE630 Computational Finance Module 6: Pricing Interest Rate Options
+\bibitem{M7} MScFE630 Computational Finance Module 7: Calibration
 

### 2020-05-11 week7/Report.tex
Grammar
WIP

@@
 \documentclass[11pt]{article}
+
+    \usepackage{listings}
 
@@
 
-In this paper we go beyond the constant risk-free continuously compounded rate.
+In this paper, we go beyond the constant risk-free continuously-compounded rate.
 There are several models to implement stochastic interest rates.
@@
 
-\section{LIBOR forward rates, stock paths, and counterparty firm values.
+\section{LIBOR Forward Rates, Stock Paths, and Counterparty Firm Values
 }
+The zero coupon bond prices are provided as observed, which means that the interest rate can be determined in the calibration process, along with the other parameters needed for the model.
+The following code sets bounds for the parameters and finds optimal values within those bounds.
+\begin{lstlisting}
+#minimizing F
+bnds = ((0,1),(0,0.2),(0,0.2), (0.00,0.10))
+opt_val = scipy.optimize.fmin_slsqp(F, (0.3, 0.05, 0.03, 0.05), bounds=bnds)
+opt_alpha = opt_val[0]
+opt_b = opt_val[1]
+opt_sigma = opt_val[2]
+opt_r0 = opt_val[3]
+\end{lstlisting}
+Running this code results in the following values for the model parameters:
+\begin{itemize}
+    \item Optimal alpha: 0.273
+    \item Optimal b: 0.069
+    \item Optimal sigma 0.028
+    \item Optimal r0: 0.075
+\end{itemize}
 
-\section{Discount factor and Value of the Option
+\section{Discount Factor and Value of the Up-and-Out Call Option
 }
+Since this is a barrier option, it is necessary to use the 'mask' function to zero the payoffs that would exceed the barrier. This is done in the payoff function.
+\begin{lstlisting}
+# define payoff for up-and-out call option
+
+def payoff(S_t, K, L):
+    stopped_S = S_t.mask(S_t > L, 0)
+    return np.maximum(stopped_S - K, 0).to_numpy()
+
+# Estimate the default-free value of the option:
+
+option_estimate = []
+option_std = []
+
+for month, path in share_prices.items():
+    payoffs = payoff(path, K, L)
+    option_price = np.exp(-risk_free*T)*payoffs
+    option_estimate.append(option_price.mean())
+    option_std.append(option_price.std()/np.sqrt(sample_size))
+\end{lstlisting}
+This calculates the mean value for the call option mean risk-free price as 1.200.
 

### 2020-05-12 week3/Report.tex
Conclusion

--- 2020-04-12 Submission1.tex
@@
     { \hspace*{\fill} \\}
+\section{Conclusion}
+In this paper, we simulated correlated firm and share price paths.
+From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price.
+Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price.
+These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference.
+These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
 
-\section{Conclusion}
-
+We are well aware that Black-Scholes formula was derived under assumptions which might not hold in a real market, as an example, if the share price deviates from the geometric Brownian motion, then our estimates can be wrong by a big margin.
+Also, our Monte Carlo estimates are highly dependant on parameters such as firm value; if firm value is well above debt value and the volatility of the firm is low, the chance of default is really low.
 \newpage
@@
 \end{thebibliography}
-\bibliographystyle{plain}
-\bibliography{template}
 

### 2020-05-12 week3/Report.tex
Delete old conclusion

@@
 These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
-
-We are well aware that Black-Scholes formula was derived under assumptions which might not hold in a real market, as an example, if the share price deviates from the geometric Brownian motion, then our estimates can be wrong by a big margin.
-Also, our Monte Carlo estimates are highly dependant on parameters such as firm value; if firm value is well above debt value and the volatility of the firm is low, the chance of default is really low.
 \newpage

### 2020-05-12 week7/Report.tex
Conclusion

@@
 \section{Conclusion}
+In this paper, we simulated correlated firm and share price paths.
+From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price.
+Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price.
+These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference.
+These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
 

### 2020-05-12 week7/Report.tex
Report Compiled

--- 2020-05-10 week7/Report.tex
@@
 
-\section{LIBOR forward rates, stock paths, and counterparty firm values.
+\section{LIBOR Forward Rates, Stock Paths, and Counterparty Firm Values
 }
 
-\section{Discount factor and Value of the Option
+In this part, we use a sample size of 100000, jointly simulate LIBOR forward rates, stock paths, and counterparty firm values.
+We assume that the counterparty firm and stock values are uncorrelated with LIBOR forward rates.
+
+\subsection{Calibrate LIBOR forward rate model from zero coupon bond prices
 }
 
+    We initialize the given zero-coupon bond prices:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{4}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{t} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{linspace}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{l+m+mi}{13}\PY{p}{)}
+
+\PY{n}{market\PYZus{}zcb\PYZus{}prices} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{l+m+mf}{1.0}\PY{p}{,} \PY{l+m+mf}{0.9938}\PY{p}{,} \PY{l+m+mf}{0.9876}\PY{p}{,} \PY{l+m+mf}{0.9815}\PY{p}{,} \PY{l+m+mf}{0.9754}\PY{p}{,} \PY{l+m+mf}{0.9694}\PY{p}{,} \PY{l+m+mf}{0.9634}\PY{p}{,} \PY{l+m+mf}{0.9574}\PY{p}{,} \PY{l+m+mf}{0.9516}\PY{p}{,}
+       \PY{l+m+mf}{0.9457}\PY{p}{,} \PY{l+m+mf}{0.9399}\PY{p}{,} \PY{l+m+mf}{0.9342}\PY{p}{,} \PY{l+m+mf}{0.9285}\PY{p}{]}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We next create functions to calculate the simulated bond prices from the
+Vasicek model (as well as helper functions A and D). We also define
+function F which is the differences between the bond prices calculated
+by our model and actual market zero-coupon bond prices:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{5}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,} \PY{n}{t2}\PY{p}{,} \PY{n}{alpha}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{alpha}\PY{o}{*}\PY{p}{(}\PY{n}{t2}\PY{o}{\PYZhy{}}\PY{n}{t1}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{alpha}
+\PY{k}{def} \PY{n+nf}{D}\PY{p}{(}\PY{n}{t1}\PY{p}{,} \PY{n}{t2}\PY{p}{,} \PY{n}{alpha}\PY{p}{,} \PY{n}{b}\PY{p}{,} \PY{n}{sigma}\PY{p}{)}\PY{p}{:}
+    \PY{n}{val1} \PY{o}{=} \PY{p}{(}\PY{n}{t2}\PY{o}{\PYZhy{}}\PY{n}{t1}\PY{o}{\PYZhy{}}\PY{n}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,}\PY{n}{t2}\PY{p}{,}\PY{n}{alpha}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{alpha}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{b}\PY{p}{)}
+    \PY{n}{val2} \PY{o}{=} \PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,}\PY{n}{t2}\PY{p}{,}\PY{n}{alpha}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{alpha}\PY{p}{)}
+    \PY{k}{return} \PY{n}{val1}\PY{o}{\PYZhy{}}\PY{n}{val2}
+
+\PY{k}{def} \PY{n+nf}{bond\PYZus{}price\PYZus{}fun}\PY{p}{(}\PY{n}{r}\PY{p}{,}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{,} \PY{n}{alpha}\PY{p}{,} \PY{n}{b}\PY{p}{,} \PY{n}{sigma}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{A}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{,}\PY{n}{alpha}\PY{p}{)}\PY{o}{*}\PY{n}{r}\PY{o}{+}\PY{n}{D}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{,}\PY{n}{alpha}\PY{p}{,}\PY{n}{b}\PY{p}{,}\PY{n}{sigma}\PY{p}{)}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{F}\PY{p}{(}\PY{n}{x}\PY{p}{)}\PY{p}{:}
+    \PY{n}{alpha} \PY{o}{=} \PY{n}{x}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
+    \PY{n}{b} \PY{o}{=} \PY{n}{x}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
+    \PY{n}{sigma} \PY{o}{=} \PY{n}{x}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}
+    \PY{n}{r0} \PY{o}{=} \PY{n}{x}\PY{p}{[}\PY{l+m+mi}{3}\PY{p}{]}
+    \PY{k}{return} \PY{n+nb}{sum}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{abs}\PY{p}{(}\PY{n}{bond\PYZus{}price\PYZus{}fun}\PY{p}{(}\PY{n}{r0}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{n}{t}\PY{p}{,}\PY{n}{alpha}\PY{p}{,}\PY{n}{b}\PY{p}{,}\PY{n}{sigma}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{market\PYZus{}zcb\PYZus{}prices}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We use the fmin\_slsqp function from scipy to calculate the optimal
+model parameters, with a minimum value of F
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{6}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{}minimizing F}
+\PY{n}{bnds} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{,}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,}\PY{l+m+mf}{0.2}\PY{p}{)}\PY{p}{,}\PY{p}{(}\PY{l+m+mi}{0}\PY{p}{,}\PY{l+m+mf}{0.2}\PY{p}{)}\PY{p}{,} \PY{p}{(}\PY{l+m+mf}{0.00}\PY{p}{,}\PY{l+m+mf}{0.10}\PY{p}{)}\PY{p}{)}
+\PY{n}{opt\PYZus{}val} \PY{o}{=} \PY{n}{scipy}\PY{o}{.}\PY{n}{optimize}\PY{o}{.}\PY{n}{fmin\PYZus{}slsqp}\PY{p}{(}\PY{n}{F}\PY{p}{,} \PY{p}{(}\PY{l+m+mf}{0.3}\PY{p}{,} \PY{l+m+mf}{0.05}\PY{p}{,} \PY{l+m+mf}{0.03}\PY{p}{,} \PY{l+m+mf}{0.05}\PY{p}{)}\PY{p}{,} \PY{n}{bounds}\PY{o}{=}\PY{n}{bnds}\PY{p}{)}
+\PY{n}{opt\PYZus{}alpha} \PY{o}{=} \PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}
+\PY{n}{opt\PYZus{}b} \PY{o}{=} \PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}
+\PY{n}{opt\PYZus{}sigma} \PY{o}{=} \PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}
+\PY{n}{opt\PYZus{}r0} \PY{o}{=} \PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{3}\PY{p}{]}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Optimization terminated successfully.    (Exit mode 0)
+            Current function value: 0.0002564991813429618
+            Iterations: 10
+            Function evaluations: 74
+            Gradient evaluations: 10
+    \end{Verbatim}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{7}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Optimal alpha: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Optimal b: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Optimal sigma }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{2}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Optimal r0: }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{opt\PYZus{}val}\PY{p}{[}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Optimal alpha: 0.273
+Optimal b: 0.069
+Optimal sigma 0.028
+Optimal r0: 0.075
+    \end{Verbatim}
+
+    We plot the actual market bond prices, with model-derived bond prices,
+and they look like a close fit.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{8}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{model\PYZus{}prices} \PY{o}{=} \PY{n}{bond\PYZus{}price\PYZus{}fun}\PY{p}{(}\PY{n}{opt\PYZus{}r0}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{n}{t}\PY{p}{,} \PY{n}{opt\PYZus{}alpha}\PY{p}{,} \PY{n}{opt\PYZus{}b}\PY{p}{,} \PY{n}{opt\PYZus{}sigma}\PY{p}{)}
+\PY{n}{model\PYZus{}yield} \PY{o}{=} \PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{model\PYZus{}prices}\PY{p}{)}\PY{o}{/}\PY{n}{t}
+
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{market\PYZus{}zcb\PYZus{}prices}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Market Prices}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{t}\PY{p}{,} \PY{n}{model\PYZus{}prices}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Calibrated Prices}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_15_1.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+\subsection{Simulate LIBOR rate paths
+}
+
+    We first initialize the parameter \(\sigma_j\)
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{9}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{sigmaj} \PY{o}{=} \PY{l+m+mf}{0.2}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We use paramters we obtained above to recreate the Vasicek bond prices:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{10}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,} \PY{n}{t2}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{opt\PYZus{}alpha}\PY{o}{*}\PY{p}{(}\PY{n}{t2}\PY{o}{\PYZhy{}}\PY{n}{t1}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{opt\PYZus{}alpha}
+
+\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{t1}\PY{p}{,} \PY{n}{t2}\PY{p}{)}\PY{p}{:}
+    \PY{n}{val1} \PY{o}{=} \PY{p}{(}\PY{n}{t2}\PY{o}{\PYZhy{}}\PY{n}{t1}\PY{o}{\PYZhy{}}\PY{n}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,}\PY{n}{t2}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{opt\PYZus{}sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{opt\PYZus{}alpha}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{opt\PYZus{}b}\PY{p}{)}
+    \PY{n}{val2} \PY{o}{=} \PY{n}{opt\PYZus{}sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{A}\PY{p}{(}\PY{n}{t1}\PY{p}{,}\PY{n}{t2}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{4}\PY{o}{*}\PY{n}{opt\PYZus{}alpha}\PY{p}{)}
+    \PY{k}{return} \PY{n}{val1} \PY{o}{\PYZhy{}} \PY{n}{val2}
+
+\PY{k}{def} \PY{n+nf}{bond\PYZus{}price}\PY{p}{(}\PY{n}{r}\PY{p}{,}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{)}\PY{p}{:}
+    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{A}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{r}\PY{o}{+}\PY{n}{C}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{T}\PY{p}{)}\PY{p}{)}
+
+\PY{n}{vasi\PYZus{}bond} \PY{o}{=} \PY{n}{bond\PYZus{}price}\PY{p}{(}\PY{n}{opt\PYZus{}r0}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{t}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    The prices calculated from the Vasicek model are close to the ZCB prices
+given by the assignment:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{11}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{n}{vasi\PYZus{}bond}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+[1.         0.99377572 0.98760087 0.98147516 0.97539831 0.96936998
+ 0.96338983 0.95745752 0.95157266 0.94573489 0.93994381 0.93419901
+ 0.9285001 ]
+    \end{Verbatim}
+
+    We now initialize the matrices we will use to store the Monte Carlo
+simulations, for both basic Monte Carlo and Predictor-Corrector method.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{12}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{n\PYZus{}simulations} \PY{o}{=} \PY{n}{sample\PYZus{}size}
+\PY{n}{n\PYZus{}steps} \PY{o}{=} \PY{n+nb}{len}\PY{p}{(}\PY{n}{t}\PY{p}{)}
+
+\PY{n}{mc\PYZus{}forward} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones}\PY{p}{(}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,} \PY{n}{n\PYZus{}steps}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{\PYZhy{}}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]}\PY{p}{)}
+\PY{n}{predcorr\PYZus{}forward} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones}\PY{p}{(}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,} \PY{n}{n\PYZus{}steps}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{\PYZhy{}}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n}{vasi\PYZus{}bond}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]}\PY{p}{)}
+\PY{n}{predcorr\PYZus{}capfac} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones}\PY{p}{(}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,} \PY{n}{n\PYZus{}steps}\PY{p}{]}\PY{p}{)}
+\PY{n}{mc\PYZus{}capfac} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones}\PY{p}{(}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,} \PY{n}{n\PYZus{}steps}\PY{p}{]}\PY{p}{)}
+
+\PY{n}{delta} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{ones}\PY{p}{(}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,} \PY{n}{n\PYZus{}steps} \PY{o}{\PYZhy{}} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{t}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]}\PY{o}{\PYZhy{}}\PY{n}{t}\PY{p}{[}\PY{p}{:}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We now run the Monte Carlo simulation for each time step:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{13}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{n\PYZus{}steps}\PY{p}{)}\PY{p}{:}
+    \PY{n}{Z} \PY{o}{=} \PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size}\PY{o}{=}\PY{p}{[}\PY{n}{n\PYZus{}simulations}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}
+
+    \PY{n}{muhat} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{mc\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{mc\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+    \PY{n}{mc\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{n}{mc\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{muhat}\PY{o}{\PYZhy{}}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{+}\PY{n}{sigmaj}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}
+
+    \PY{n}{mu\PYZus{}initial} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{predcorr\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{predcorr\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+    \PY{n}{for\PYZus{}temp} \PY{o}{=} \PY{n}{predcorr\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{mu\PYZus{}initial}\PY{o}{\PYZhy{}}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{+}\PY{n}{sigmaj}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}
+    \PY{n}{mu\PYZus{}term} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{for\PYZus{}temp}\PY{o}{*}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{for\PYZus{}temp}\PY{p}{)}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+    \PY{n}{predcorr\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{n}{predcorr\PYZus{}forward}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{mu\PYZus{}initial}\PY{o}{+}\PY{n}{mu\PYZus{}term}\PY{o}{\PYZhy{}}\PY{n}{sigmaj}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{o}{/}\PY{l+m+mi}{2}\PY{o}{+}\PY{n}{sigmaj}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{delta}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{n}{i}\PY{p}{:}\PY{p}{]}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    From our Monte Carlo simulation, we now calculate the capitalization
+factors and bond prices, and plot them to compare them with the Vasicek
+bond prices.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{14}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{mc\PYZus{}capfac}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{cumprod}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{mc\PYZus{}forward}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+\PY{n}{predcorr\PYZus{}capfac}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{:}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{cumprod}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{predcorr\PYZus{}forward}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{1}\PY{p}{)}
+
+\PY{n}{mc\PYZus{}price} \PY{o}{=} \PY{n}{mc\PYZus{}capfac}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+\PY{n}{predcorr\PYZus{}price} \PY{o}{=} \PY{n}{predcorr\PYZus{}capfac}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+
+\PY{n}{mc\PYZus{}final} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{mc\PYZus{}price}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
+\PY{n}{predcorr\PYZus{}final} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{n}{predcorr\PYZus{}price}\PY{p}{,} \PY{n}{axis}\PY{o}{=}\PY{l+m+mi}{0}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{15}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Maturity}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Bond Price}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{vasi\PYZus{}bond}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Vasicek Bond Prices}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{t}\PY{p}{,} \PY{n}{mc\PYZus{}final}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{o}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Simple Monte Carlo Bond Prices}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{t}\PY{p}{,} \PY{n}{predcorr\PYZus{}final}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{x}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Predictor\PYZhy{}Corrector Bond Prices}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
+\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_29_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    From our simulation of forward rates (we take the Predictor-Corrector
+method, we use the formula
+\(e^{r_{t_i} (t_{i+1}-t_i)} = 1 + L(t_i,t_{i+1})(t_{i+1}-t_i)\) to
+obtain the continuous compounded interest rates:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{16}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{r\PYZus{}sim} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{l+m+mi}{1} \PY{o}{+} \PY{n}{predcorr\PYZus{}forward}\PY{o}{*}\PY{p}{(}\PY{n}{delta}\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{n}{delta}
+\end{Verbatim}
+\end{tcolorbox}
+
+    We also calculate an annualized form of the interest rates:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{17}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{r\PYZus{}sim\PYZus{}annualized} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{r\PYZus{}sim}\PY{o}{/}\PY{n}{delta}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{18}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{r\PYZus{}sim\PYZus{}annualized}
+\end{Verbatim}
+\end{tcolorbox}
+
+            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
+\prompt{Out}{outcolor}{18}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+              0         1         2         3         4         5         6  \textbackslash{}
+0       0.07514  0.066032  0.073336  0.075253  0.065992  0.066157  0.066794
+1       0.07514  0.072083  0.076464  0.081468  0.079424  0.082719  0.085049
+2       0.07514  0.078051  0.079510  0.077283  0.080866  0.078631  0.085738
+3       0.07514  0.067973  0.066249  0.068189  0.061341  0.061618  0.058422
+4       0.07514  0.068828  0.067538  0.068650  0.064811  0.064151  0.067009
+{\ldots}         {\ldots}       {\ldots}       {\ldots}       {\ldots}       {\ldots}       {\ldots}       {\ldots}
+999995  0.07514  0.080051  0.081460  0.080036  0.078720  0.085394  0.090455
+999996  0.07514  0.075648  0.076774  0.074305  0.081762  0.077945  0.075159
+999997  0.07514  0.080705  0.077654  0.076033  0.068839  0.066677  0.062133
+999998  0.07514  0.085071  0.085031  0.082831  0.083125  0.087771  0.077675
+999999  0.07514  0.079983  0.080474  0.078617  0.073621  0.071960  0.072492
+
+               7         8         9        10        11
+0       0.071269  0.076366  0.074026  0.080224  0.076966
+1       0.085452  0.094079  0.106641  0.120261  0.116014
+2       0.082785  0.072790  0.076300  0.066587  0.063343
+3       0.061475  0.058621  0.057793  0.058849  0.054900
+4       0.063756  0.062794  0.065755  0.066556  0.072365
+{\ldots}          {\ldots}       {\ldots}       {\ldots}       {\ldots}       {\ldots}
+999995  0.091226  0.086187  0.086976  0.081274  0.075437
+999996  0.079487  0.069895  0.067660  0.062574  0.059106
+999997  0.059384  0.056089  0.055484  0.056012  0.054232
+999998  0.075775  0.075541  0.073908  0.078261  0.073692
+999999  0.068380  0.066112  0.071977  0.071854  0.065560
+
+[1000000 rows x 12 columns]
+\end{Verbatim}
+\end{tcolorbox}
+
+\subsection{Generate stock and firm values
+}
+
+    Similar to the first groupwork assignment, we use a Cholesky
+decomposition to generate the correlated price paths
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{19}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{k}{def} \PY{n+nf}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{dT}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
+
+    \PY{k}{if} \PY{n}{varying\PYZus{}vol}\PY{p}{:}
+        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+    \PY{k}{else}\PY{p}{:}
+        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
+
+    \PY{k}{return} \PY{n}{prev\PYZus{}price}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{r}\PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{sigma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
+
+\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{r\PYZus{}sim}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
+    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
+    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}
+
+    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r\PYZus{}sim}\PY{p}{,} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+
+    \PY{n}{first\PYZus{}row} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{p}{[}\PY{n}{S0}\PY{p}{]}\PY{o}{*}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+    \PY{n}{first\PYZus{}row} \PY{o}{=} \PY{n}{first\PYZus{}row}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{concat}\PY{p}{(}\PY{p}{[}\PY{n}{first\PYZus{}row}\PY{p}{,} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{]}\PY{p}{)}
+    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{reset\PYZus{}index}\PY{p}{(}\PY{n}{drop}\PY{o}{=}\PY{k+kc}{True}\PY{p}{)}
+
+    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{r\PYZus{}sim}\PY{p}{,} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{)}\PY{p}{)}
+    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+
+    \PY{n}{first\PYZus{}row} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{p}{[}\PY{n}{v\PYZus{}0}\PY{p}{]}\PY{o}{*}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+    \PY{n}{first\PYZus{}row} \PY{o}{=} \PY{n}{first\PYZus{}row}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
+    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{concat}\PY{p}{(}\PY{p}{[}\PY{n}{first\PYZus{}row}\PY{p}{,} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}\PY{p}{)}
+    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{reset\PYZus{}index}\PY{p}{(}\PY{n}{drop}\PY{o}{=}\PY{k+kc}{True}\PY{p}{)}
+
+    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{20}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}prices}\PY{p}{,} \PY{n}{firm\PYZus{}prices} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{r\PYZus{}sim\PYZus{}annualized}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+We also plot the first 1000 stock price and firm value paths simulated:
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{23}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{share\PYZus{}prices}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{:}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Share price over 12 months}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_43_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{24}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{firm\PYZus{}prices}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{:}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{title}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Firm price over 12 months}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{legend}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}\PY{p}{;}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{center}
+    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_44_0.png}
+    \end{center}
+    { \hspace*{\fill} \\}
+
+\section{Discount Factor and Value of the Up-and-Out Call Option
+}
+
+In this section we use the capitalisation factor calculated in the section aboove to  calculate the one-year discount factor which applies for each simulation, and use this to find first the value of the option for the jointly simulated stock and firm paths with no default risk, and then the value of the option with counterparty default risk.
+\\
+
+We first calculated the one year discount factor, by inverting the capitalisation factor.
+The capitalisation factor is calculated by taking the cumulative product of the interest rate between each timestep.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{25}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{one\PYZus{}year\PYZus{}disc\PYZus{}fac} \PY{o}{=} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{cumprod}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{+}\PY{n}{r\PYZus{}sim}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}
+\PY{n}{one\PYZus{}year\PYZus{}disc\PYZus{}fac}
+\end{Verbatim}
+\end{tcolorbox}
+
+            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
+\prompt{Out}{outcolor}{25}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+array([0.93045792, 0.91464088, 0.92665426, {\ldots}, 0.93658426, 0.92383486,
+       0.92979433])
+\end{Verbatim}
+\end{tcolorbox}
+
+Next, we calculate the Default-Free Option Value. One difference is that we multiple the payoff by the one year discount factor, instead of multiplying with  $e^{rT}$
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{26}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
+\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
+    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
+    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{27}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{c+c1}{\PYZsh{} Estimate the default\PYZhy{}free value of the option:}
+\PY{n}{option\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+\PY{n}{option\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
+
+\PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}prices}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+\PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{one\PYZus{}year\PYZus{}disc\PYZus{}fac}\PY{o}{*}\PY{n}{payoffs}
+\PY{n}{option\PYZus{}estimate} \PY{o}{=} \PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}
+\PY{n}{option\PYZus{}std} \PY{o}{=} \PY{n}{option\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{28}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Default\PYZhy{}free option price }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{option\PYZus{}estimate}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Default\PYZhy{}free option price standard deviation }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{option\PYZus{}std}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Default-free option price 8.296
+Default-free option price standard deviation 0.008
+    \end{Verbatim}
+
+Next, we incorporate the CVA Adjustment similar to the first submission.
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{29}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}prices}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
+\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}prices}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
+\PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{one\PYZus{}year\PYZus{}disc\PYZus{}fac}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
+\PY{n}{cva\PYZus{}estimate} \PY{o}{=} \PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}
+\PY{n}{cva\PYZus{}std} \PY{o}{=} \PY{n}{amount\PYZus{}lost}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+
+\PY{n}{option\PYZus{}cva\PYZus{}price} \PY{o}{=} \PY{n}{option\PYZus{}price} \PY{o}{\PYZhy{}} \PY{n}{amount\PYZus{}lost}
+\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}
+\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{n}{option\PYZus{}cva\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
+\prompt{In}{incolor}{30}{\boxspacing}
+\begin{Verbatim}[commandchars=\\\{\}]
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Credit value adjustment }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{cva\PYZus{}estimate}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Credit value adjustment standard deviation }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{cva\PYZus{}std}\PY{p}{)}\PY{p}{)}
+
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA\PYZhy{}adjusted option price }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices}\PY{p}{)}\PY{p}{)}
+\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CVA\PYZhy{}adjusted option price standard deviation }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std}\PY{p}{)}\PY{p}{)}
+\end{Verbatim}
+\end{tcolorbox}
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Credit value adjustment 0.018
+Credit value adjustment standard deviation 0.000
+CVA-adjusted option price 8.278
+CVA-adjusted option price standard deviation 0.008
+    \end{Verbatim}
+
 \section{Conclusion}
+In this paper, we simulated correlated firm and share price paths.
+From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price.
+Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price.
+These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference.
+These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
 

### 2020-05-12 week7/Report.tex
Added More Citations

@@
 In this paper, we simulated correlated firm and share price paths.
-From this, we priced an up-and-out call option at 8.299 with a default-free risk profile, and at 8.281 for the CVA-adjusted price.
+From this, we priced an up-and-out call option at 8.296 with a default-free risk profile, and at 8.278 for the CVA-adjusted price.
 Considering that the same parameters are used as the first submission, where the Black-Scholes-Merton model was used to arrive at a price of 5.697, we observe that both the default risk, the variable interest rate and local volatility have all added a premium to the option price.
-These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2\% of the difference.
+These conditions, which are more aligned to observed market conditions, gave a total increase of 45\% over the previously calculated price, with the default risk accounting for only 0.2 of the difference.
 These results underline the importance of choosing the correct model and performing accurate calibration in order to calculate instrument prices.
@@
 \bibitem{CIR1} Cox, J. C., Ingersoll Jr, J. E. and Ross, S. A. (1985). An intertemporal general equilibrium model of asset prices, Econometrica: Journal of the Econometric Society pp. 363-384.
-\bibitem{AMST1} Albrecher, H., Mayer, P., Schoutens, W. and Tistaert, J. (2007).
-``The Little Heston Trap'', Wilmott (1): 83--92.
+\bibitem{Mer1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
 \bibitem{Cox1}  Cox, John. "Notes on option pricing I: Constant elasticity of variance diffusions." Unpublished note, Stanford University, Graduate School of Business (1975).
+\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
+\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
+\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
+\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
 \bibitem{M5} MScFE630 Computational Finance Module 5: Monte Carlo Methods for Risk Management
